### 2017-01-13 paper/paper.tex
related work

%% bare_conf.tex
%% V1.4b
%% 2015/08/26
%% by Michael Shell
%% See:
%% http://www.michaelshell.org/
%% for current contact information.
%%
%% This is a skeleton file demonstrating the use of IEEEtran.cls
%% (requires IEEEtran.cls version 1.8b or later) with an IEEE
%% conference paper.
%%
%% Support sites:
%% http://www.michaelshell.org/tex/ieeetran/
%% http://www.ctan.org/pkg/ieeetran
%% and
%% http://www.ieee.org/

%%*************************************************************************
%% Legal Notice:
%% This code is offered as-is without any warranty either expressed or
%% implied; without even the implied warranty of MERCHANTABILITY or
%% FITNESS FOR A PARTICULAR PURPOSE! 
%% User assumes all risk.
%% In no event shall the IEEE or any contributor to this code be liable for
%% any damages or losses, including, but not limited to, incidental,
%% consequential, or any other damages, resulting from the use or misuse
%% of any information contained here.
%%
%% All comments are the opinions of their respective authors and are not
%% necessarily endorsed by the IEEE.
%%
%% This work is distributed under the LaTeX Project Public License (LPPL)
%% ( http://www.latex-project.org/ ) version 1.3, and may be freely used,
%% distributed and modified. A copy of the LPPL, version 1.3, is included
%% in the base LaTeX documentation of all distributions of LaTeX released
%% 2003/12/01 or later.
%% Retain all contribution notices and credits.
%% ** Modified files should be clearly indicated as such, including  **
%% ** renaming them and changing author support contact information. **
%%*************************************************************************

% *** Authors should verify (and, if needed, correct) their LaTeX system  ***
% *** with the testflow diagnostic prior to trusting their LaTeX platform ***
% *** with production work. The IEEE's font choices and paper sizes can   ***
% *** trigger bugs that do not appear when using other class files.       ***                          ***
% The testflow support page is at:
% http://www.michaelshell.org/tex/testflow/

\documentclass[conference]{IEEEtran}
% Some Computer Society conferences also require the compsoc mode option,
% but others use the standard conference format.
%
% If IEEEtran.cls has not been installed into the LaTeX system files,
% manually specify the path to it like:
% \documentclass[conference]{../sty/IEEEtran}

% Some very useful LaTeX packages include:
% (uncomment the ones you want to load)

% *** MISC UTILITY PACKAGES ***
%
%\usepackage{ifpdf}
% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
% compilation based on whether the output is pdf or dvi.
% usage:
% \ifpdf
%   % pdf code
% \else
%   % dvi code
% \fi
% The latest version of ifpdf.sty can be obtained from:
% http://www.ctan.org/pkg/ifpdf
% Also, note that IEEEtran.cls V1.7 and later provides a builtin
% \ifCLASSINFOpdf conditional that works the same way.
% When switching from latex to pdflatex and vice-versa, the compiler may
% have to be run twice to clear warning/error messages.

% *** CITATION PACKAGES ***
%
%\usepackage{cite}
% cite.sty was written by Donald Arseneau
% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
% \cite{} output to follow that of the IEEE. Loading the cite package will
% result in citation numbers being automatically sorted and properly
% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
% \cite will automatically add leading space, if needed. Use cite.sty's
% noadjust option (cite.sty V3.8 and later) if you want to turn this off
% such as if a citation ever needs to be enclosed in parenthesis.
% cite.sty is already installed on most LaTeX systems. Be sure and use
% version 5.0 (2009-03-20) and later if using hyperref.sty.
% The latest version can be obtained at:
% http://www.ctan.org/pkg/cite
% The documentation is contained in the cite.sty file itself.

% *** GRAPHICS RELATED PACKAGES ***
%
\ifCLASSINFOpdf
  % \usepackage[pdftex]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../pdf/}{../jpeg/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
\else
  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
  % will default to the driver specified in the system graphics.cfg if no
  % driver is specified.
  % \usepackage[dvips]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../eps/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.eps}
\fi
% graphicx was written by David Carlisle and Sebastian Rahtz. It is
% required if you want graphics, photos, etc. graphicx.sty is already
% installed on most LaTeX systems. The latest version and documentation
% can be obtained at: 
% http://www.ctan.org/pkg/graphicx
% Another good source of documentation is "Using Imported Graphics in
% LaTeX2e" by Keith Reckdahl which can be found at:
% http://www.ctan.org/pkg/epslatex
%
% latex, and pdflatex in dvi mode, support graphics in encapsulated
% postscript (.eps) format. pdflatex in pdf mode supports graphics
% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
% not a bitmapped formats (.jpeg, .png). The IEEE frowns on bitmapped formats
% which can result in "jaggedy"/blurry rendering of lines and letters as
% well as large increases in file sizes.
%
% You can find documentation about the pdfTeX application at:
% http://www.tug.org/applications/pdftex

% *** MATH PACKAGES ***
%
%\usepackage{amsmath}
% A popular package from the American Mathematical Society that provides
% many useful and powerful commands for dealing with mathematics.
%
% Note that the amsmath package sets \interdisplaylinepenalty to 10000
% thus preventing page breaks from occurring within multiline equations. Use:
%\interdisplaylinepenalty=2500
% after loading amsmath to restore such page breaks as IEEEtran.cls normally
% does. amsmath.sty is already installed on most LaTeX systems. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/pkg/amsmath

% *** SPECIALIZED LIST PACKAGES ***
%
%\usepackage{algorithmic}
% algorithmic.sty was written by Peter Williams and Rogerio Brito.
% This package provides an algorithmic environment fo describing algorithms.
% You can use the algorithmic environment in-text or within a figure
% environment to provide for a floating algorithm. Do NOT use the algorithm
% floating environment provided by algorithm.sty (by the same authors) or
% algorithm2e.sty (by Christophe Fiorio) as the IEEE does not use dedicated
% algorithm float types and packages that provide these will not provide
% correct IEEE style captions. The latest version and documentation of
% algorithmic.sty can be obtained at:
% http://www.ctan.org/pkg/algorithms
% Also of interest may be the (relatively newer and more customizable)
% algorithmicx.sty package by Szasz Janos:
% http://www.ctan.org/pkg/algorithmicx

% *** ALIGNMENT PACKAGES ***
%
%\usepackage{array}
% Frank Mittelbach's and David Carlisle's array.sty patches and improves
% the standard LaTeX2e array and tabular environments to provide better
% appearance and additional user controls. As the default LaTeX2e table
% generation code is lacking to the point of almost being broken with
% respect to the quality of the end results, all users are strongly
% advised to use an enhanced (at the very least that provided by array.sty)
% set of table tools. array.sty is already installed on most systems. The
% latest version and documentation can be obtained at:
% http://www.ctan.org/pkg/array

% IEEEtran contains the IEEEeqnarray family of commands that can be used to
% generate multiline equations as well as matrices, tables, etc., of high
% quality.

% *** SUBFIGURE PACKAGES ***
%\ifCLASSOPTIONcompsoc
%  \usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
%\else
%  \usepackage[caption=false,font=footnotesize]{subfig}
%\fi
% subfig.sty, written by Steven Douglas Cochran, is the modern replacement
% for subfigure.sty, the latter of which is no longer maintained and is
% incompatible with some LaTeX packages including fixltx2e. However,
% subfig.sty requires and automatically loads Axel Sommerfeldt's caption.sty
% which will override IEEEtran.cls' handling of captions and this will result
% in non-IEEE style figure/table captions. To prevent this problem, be sure
% and invoke subfig.sty's "caption=false" package option (available since
% subfig.sty version 1.3, 2005/06/28) as this is will preserve IEEEtran.cls
% handling of captions.
% Note that the Computer Society format requires a larger sans serif font
% than the serif footnote size font used in traditional IEEE formatting
% and thus the need to invoke different subfig.sty package options depending
% on whether compsoc mode has been enabled.
%
% The latest version and documentation of subfig.sty can be obtained at:
% http://www.ctan.org/pkg/subfig

% *** FLOAT PACKAGES ***
%
%\usepackage{fixltx2e}
% fixltx2e, the successor to the earlier fix2col.sty, was written by
% Frank Mittelbach and David Carlisle. This package corrects a few problems
% in the LaTeX2e kernel, the most notable of which is that in current
% LaTeX2e releases, the ordering of single and double column floats is not
% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
% single column figure to be placed prior to an earlier double column
% figure.
% Be aware that LaTeX2e kernels dated 2015 and later have fixltx2e.sty's
% corrections already built into the system in which case a warning will
% be issued if an attempt is made to load fixltx2e.sty as it is no longer
% needed.
% The latest version and documentation can be found at:
% http://www.ctan.org/pkg/fixltx2e

%\usepackage{stfloats}
% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
% the ability to do double column floats at the bottom of the page as well
% as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
% LaTeX2e). It also provides a command:
%\fnbelowfloat
% to enable the placement of footnotes below bottom floats (the standard
% LaTeX2e kernel puts them above bottom floats). This is an invasive package
% which rewrites many portions of the LaTeX2e float routines. It may not work
% with other packages that modify the LaTeX2e float routines. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/pkg/stfloats
% Do not use the stfloats baselinefloat ability as the IEEE does not allow
% \baselineskip to stretch. Authors submitting work to the IEEE should note
% that the IEEE rarely uses double column equations and that authors should try
% to avoid such use. Do not be tempted to use the cuted.sty or midfloat.sty
% packages (also by Sigitas Tolusis) as the IEEE does not format its papers in
% such ways.
% Do not attempt to use stfloats with fixltx2e as they are incompatible.
% Instead, use Morten Hogholm'a dblfloatfix which combines the features
% of both fixltx2e and stfloats:
%
% \usepackage{dblfloatfix}
% The latest version can be found at:
% http://www.ctan.org/pkg/dblfloatfix

% *** PDF, URL AND HYPERLINK PACKAGES ***
%
%\usepackage{url}
% url.sty was written by Donald Arseneau. It provides better support for
% handling and breaking URLs. url.sty is already installed on most LaTeX
% systems. The latest version and documentation can be obtained at:
% http://www.ctan.org/pkg/url
% Basically, \url{my_url_here}.

% *** Do not adjust lengths that control margins, column widths, etc. ***
% *** Do not use packages that alter fonts (such as pslatex).         ***
% There should be no need to do such things with IEEEtran.cls V1.6 and later.
% (Unless specifically asked to do so by the journal or conference you plan
% to submit to, of course. )

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}

\begin{document}
%
% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
\title{Cyber vs Regular: Understanding the State of Consumer Fraud in America
}

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
\author{\IEEEauthorblockN{Mohammad Taha Khan and
Chris Kanich}
\IEEEauthorblockA{Department of Computer Science, University of Illinois at Chicago\\
taha@cs.uic.edu, ckanich@uic.edu}}

% conference papers do not typically use \thanks and this command
% is locked out in conference mode. If really needed, such as for
% the acknowledgment of grants, issue a \IEEEoverridecommandlockouts
% after \documentclass

% for over three affiliations, or if they all won't fit within the width
% of the page, use this alternative format:
% 
%\author{\IEEEauthorblockN{Michael Shell\IEEEauthorrefmark{1},
%Homer Simpson\IEEEauthorrefmark{2},
%James Kirk\IEEEauthorrefmark{3}, 
%Montgomery Scott\IEEEauthorrefmark{3} and
%Eldon Tyrell\IEEEauthorrefmark{4}}
%\IEEEauthorblockA{\IEEEauthorrefmark{1}School of Electrical and Computer Engineering\\
%Georgia Institute of Technology,
%Atlanta, Georgia 30332--0250\\ Email: see http://www.michaelshell.org/contact.html}
%\IEEEauthorblockA{\IEEEauthorrefmark{2}Twentieth Century Fox, Springfield, USA\\
%Email: homer@thesimpsons.com}
%\IEEEauthorblockA{\IEEEauthorrefmark{3}Starfleet Academy, San Francisco, California 96678-2391\\
%Telephone: (800) 555--1212, Fax: (888) 555--1212}
%\IEEEauthorblockA{\IEEEauthorrefmark{4}Tyrell Inc., 123 Replicant Street, Los Angeles, California 90210--4321}}

% use for special paper notices
%\IEEEspecialpapernotice{(Invited Paper)}

% make the title area
\maketitle

% As a general rule, do not put math, special symbols or citations
% in the abstract
\begin{abstract}
The abstract goes here.
\end{abstract}

% no keywords

% For peer review papers, you can put extra information on the cover
% page as needed:
% \ifCLASSOPTIONpeerreview
% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
% \fi
%
% For peerreview papers, this IEEEtran command inserts a page break and
% creates the second title. It will be ignored for other modes.
\IEEEpeerreviewmaketitle

\section{Introduction}
the main contributions:
Understanding the differences in the  nature of cyber and regular frauds in the United States.
Exploring if certain demographics are more succeptible to cybercrime
Suggesting improvements that might be the right way to create more awareness annd campaings.

Fraud and and deceptive practices have been around since the establishment of

The FTC and the FBI

According to a recent FTC survey report\cite{ftcfraud} shows that Intenet fraud had doubled within the past 6 years and now is the top most source of frauds within the the US.

Explain regualr and cyber fraud... dive details in categotization

\section{Related Work}

As our work evaluates both cyber as well as regular frauds, we provide related work that encompas both of these categories. However, we elaborate more on recent research that focuses on cyber frauds due to the increased Internet usage trends for sensitive activities leading to more individuals being vicitms of online frauds \cite{ftcfraud}. Before the Internet became a primarey source of economic and social acticity, resreaches measured \cite{ukphone} and developed techniques based on statisitical models \cite{creditfraud, phoenfraudnn, phonefraudstat} to detect phone and credit card based frauds. In the past few years, most research has shifted focus towards cyber activity \cite{databreach, playingfield, fraudfinance, cybertrends} due to its high potential for harm.

Even though, term \emph{"cyber"} is usually associated with Computer Science, due to its recent socio-economic impact, reseachers in Economics, Law and Finance have also explored for solutions to this problem by incorporating methodologies specific to their areas. Ionescu et. al \cite{fraudfinance} charectarize the types and sources cyber frauds in global digital netowrks. The authors link the exponential increase of cyber fraud to increased Internet usage for financial management and transactions, especially in financial markets. They suggest the involement of all stakeholders and employees through awareness and training for contiaining and mitigating this type of fraud. Similarly, Howard et. al \cite{cybertrends} study malicious code attacks against financial networks and suggest technical detection and mitigation techniques for financial infrastructure. \cite{playingfield} studies how the cyber criminals have several potential advantages over the law enforcement agencies that they are opposing them. They suggest some practical steps to even out the differential gap.

Due to an increase in overall concern for online crimimal activity, there have also been state sponsered research that look af Fra have Smyth et. al \cite{fraudcanada} measured the extent of cyber fraud in Canada in 2011. Their work indicated that a major chunk of frauds do not get recorded and suggested a need of a sentinel to record fraud data similar to the FTC complaint center in the US.

Another siginficnat area of research focuses on understanding the underlying demographics of vitcims of these frauds. A recent FTC Report \cite{ftccomplaints} use complaint data to evaluate qunatify complaint rates and nature across different ethinic and education groups. Reseachers in \cite{databreach} provide a comprehensive survey report collected from individials that were victims of an online data breach. They categorize their results in different income, education, age and ethinic groups. Such reseach aims at allowing organizations to better develop policies and create awarenerss among for consumer rights protections.

In comparison to previous reseach which study either cyber of regular fraud, our work provides a different angle of evaluation byat charectarizing both types of frauds and provide distinctions for each category based on popular demographics.

Our study mainly fo

\section{Data Collection}

\section{Evaluation}

\section{Discussion}

\section{Conclusion}
The conclusion goes here.

\section*{Acknowledgment}

The authors would like to thank...

\begin{thebibliography}{1}

\bibitem{IEEEhowto:kopka}
H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.

\bibitem{affiliate}
pete snyder affiliate fraud

\bibitem{fraudfinance}
cyberfraud in a global digital network

\bibitem{databreach}
Consumer Attitudes Toward Data Breach Noti cations and Loss of Personal Information

\bibitem{playingfield}
An Uneven Playing Field: The Advantages of the Cyber Criminal vs. Law Enforcement-and Some Practical

\bibitem{identitytheft}
Identity Theft as a Teachable Moment

\bibitem{cybertrends}
Cyber Fraud Trends and Mitigation

\bibitem{fraudcanada}
Cyberfraud in Canada

\bibitem{ukphone}
Controlling Cell Phone Fraud in the US: Lessons for the UK ‘Foresight’ Prevention Initiative

\bibitem{creditfraud}
Neural data mining for credit card fraud detection

\bibitem{phoenfraudnn}
Detection of mobile phone fraud using supervised neural networks: A first prototype

\bibitem{phonefraudstat}
Statistical Fraud Detection: A Review

\bibitem{ftcfraud}
http://gotaclassaction.com/wp-content/uploads/2013/05/FTC-Fraud-Survey.pdf

\bibitem{ftccomplaints}
complaints ftc

\end{thebibliography}

% that's all folks
\end{document}

### 2017-01-13 src/dump_db.py

@@ -46,10 +46,10 @@ def is_cyber( contactmethod, fraudtype):
 def add_ftc_data():
 	cursor.execute(
 	'''
-		CREATE TABLE ftc_data(
+		CREATE TABLE complaints(
 			Organization TEXT, 
-        	CustomerZip NUMERIC, 
-        	FraudZip NUMERIC, 
+        	CustomerZip TEXT, 
+        	FraudZip TEXT, 
         	ReportingMethod TEXT,
         	SecReportingMethod TEXT,
         	FraudType TEXT,
@@ -75,18 +75,114 @@ def add_ftc_data():
 	  		IsCyber = is_cyber(ReportingMethod, FraudType)
 
 	  		data = (Organization, CustomerZip, FraudZip, ReportingMethod, SecReportingMethod, FraudType, FraudDate, ReportingDate, IsCyber)
+	  		cursor.execute("INSERT INTO complaints VALUES %s " % str(data))
 
-	  		cursor.execute("INSERT INTO ftc_data VALUES %s " % str(data))
 
+
+
+def add_income_data():
+	cursor.execute(
+	'''
+		CREATE TABLE incomes(
+			ZipCode TEXT PRIMARY KEY,
+			Employment INT, 
+        	MedianIncome INT)
+    ''')
+
+	connection.commit()
+
+	with open(os.path.join(DATA_PATH, 'income_data.csv')) as csvfile:
+	  	reader = csv.DictReader(csvfile)
+	  	for line in reader:
+
+	  		ZipCode = line['GEO.display-label'].split(" ")[1]
+	  		Employment  = line['HC01_VC03']
+	  		MedianIncome = line['HC01_VC85']
+
+	  		data = (ZipCode, Employment, MedianIncome)
+	  		cursor.execute("INSERT INTO incomes VALUES %s " % str(data))
 
 
 def add_population_data():
-	print("aa")
+	cursor.execute(
+	'''
+		CREATE TABLE populations(
+			ZipCode TEXT PRIMARY KEY,
+			Population INT)
+    ''')
 
-def main():
-	add_ftc_data()
 	connection.commit()
 
+	with open(os.path.join(DATA_PATH, 'population_data.csv')) as csvfile:
+	  	reader = csv.DictReader(csvfile)
+	  	for line in reader:
+
+	  		ZipCode = line['GEO.display-label'].split(" ")[1]
[…]

### 2017-01-14 src/dump_db.py
data sources added to text

@@ -44,41 +44,48 @@ def is_cyber( contactmethod, fraudtype):
 
 
 def add_ftc_data():
-	cursor.execute(
-	'''
-		CREATE TABLE complaints(
-			Organization TEXT, 
-        	CustomerZip TEXT, 
-        	FraudZip TEXT, 
-        	ReportingMethod TEXT,
-        	SecReportingMethod TEXT,
-        	FraudType TEXT,
-        	FraudDate DATE,
-        	ReportingDate DATE,
-        	IsCyber BOOLEAN)
-    ''')
+		count = 0
+		cursor.execute(
+		'''
+			CREATE TABLE complaints(
+				Organization TEXT, 
+	        	CustomerZip TEXT, 
+	        	FraudZip TEXT, 
+	        	ContactMethod TEXT,
+	        	SecContactMethod TEXT,
+	        	FraudType TEXT,
+	        	FraudDate DATE,
+	        	ReportingDate DATE,
+	        	IsCyber BOOLEAN,
+	        	Month TEXT,
+	        	Year TEXT)
+	    ''')
 
-	connection.commit()
+		connection.commit()
 
-	with open(os.path.join(DATA_PATH, 'ftc_data.csv')) as csvfile:
-	  	reader = csv.DictReader(csvfile)
-	  	for line in reader:
+		with open(os.path.join(DATA_PATH, 'ftc_data.csv')) as csvfile:
+		  	reader = csv.DictReader(csvfile)
+		  	for line in reader:
+		  		try:
 
-	  		Organization = line['OrganizationName']
-	  		CustomerZip = callibrate_zip(line['Consumer-ZipCode'])
-	  		FraudZip = callibrate_zip(line['Company-ZipCode'])
-	  		ReportingMethod = line['InitialContactMethodDesc']
-	  		SecReportingMethod = line['AgencyContactMethodDesc']
-	  		FraudType = line['ProductCodeDesc']
-	  		FraudDate = line['InitialContactDate']
-	  		ReportingDate = line['AgencyContactDate']
-	  		IsCyber = is_cyber(ReportingMethod, FraudType)
+			  		Organization = line['OrganizationName']
+			  		CustomerZip = callibrate_zip(line['Consumer-ZipCode'])
+			  		FraudZip = callibrate_zip(line['Company-ZipCode'])
+			  		ContactMethod = line['InitialContactMethodDesc']
+			  		SecContactMethod = line['AgencyContactMethodDesc']
[…]

### 2017-01-15 plots/reporting_methods.m
working on evaluation

@@ -1,0 +1,10 @@
+x = [1,2];
+% 
+% y = [1,2,3,4;...
+%      5,6,7,8];
+y = [33.35, 66.64; 82.18 17.81];
+
+figure;
+barh(x,y,'stacked'); % stacks values in each row together
+title('Stacked Style')
+

### 2017-01-15 plots/temporal_day.m

@@ -1,0 +1,19 @@
+% holoiday crimes
+cyb_h =sum(cyber(349:369))
+reg_h =sum(reg(349:369))
+
+%regular crimes
+cyb_n =sum(cyber(227:247))
+reg_n =sum(reg(227:247))
+
+y = [cyb_n reg_n; cyb_h reg_h;];
+b = bar(y, 'r', 'EdgeColor',[0 0 0],'LineWidth',1.5, 'BarWidth', 0.5)
+
+b(2).FaceColor = 'b';
+legend('Cyber','Regular', 'Location','northeast', 'FontSize', 25)
+set(gca,'FontSize', 11)
+set(gca,'xtick',[])
+set(gcf, 'PaperPosition', [0 0 10 6]); %Position plot at left hand corner with width 5 and height 5.
+set(gcf, 'PaperSize', [10 6]); %Set the paper to have width 5 and height 5.
+%axis([0 128 0 280])
+saveas(gcf, 'reg_vs_holiday', 'pdf') %Save figure

### 2017-01-15 src/1_temporal_day.py

@@ -1,0 +1,46 @@
+# The main sripts that dumps all the datasets into the tables for querying
+import os
+import csv
+import sqlite3
+
+
+DATA_PATH  = "./data"
+OUT_PATH = "../plots"
+
+
+csv_file = open(os.path.join(OUT_PATH, '1_temporal_day.csv'), "w")
+data_writer = csv.writer(csv_file,delimiter=',')
+
+connection = sqlite3.connect('project_data.db')
+cursor = connection.cursor()
+
+cursor.execute(
+		'''
+			SELECT Count(Day), Day, Month, Year FROM complaints
+			WHERE IsCyber = 1
+			GROUP BY Year, Month, Day
+			ORDER BY Year ASC, Month ASC, Day ASC
+
+	    ''')
+
+cyber_rows = cursor.fetchall()
+
+cursor.execute(
+		'''
+			SELECT Count(Day), Day, Month, Year FROM complaints
+			WHERE IsCyber = 0
+			GROUP BY Year, Month, Day
+			ORDER BY Year ASC, Month ASC, Day ASC
+
+	    ''')
+reg_rows = cursor.fetchall()
+
+for i in reg_rows:
+	for j in cyber_rows:
+
+		if str(list(i)[1:4]) == str(list(j)[1:4]):
+			new_date = str(list(i)[3])+str(list(i)[2])+str(list(i)[1])
+			new_row = [new_date, i[0], j[0]]
+			data_writer.writerow(new_row)
+
+

### 2017-01-15 src/2_temporal_month.py

@@ -1,0 +1,47 @@
+# The main sripts that dumps all the datasets into the tables for querying
+import os
+import csv
+import sqlite3
+
+
+DATA_PATH  = "./data"
+OUT_PATH = "../plots"
+
+
+csv_file = open(os.path.join(OUT_PATH, '2_temporal_month.csv'), "w")
+data_writer = csv.writer(csv_file,delimiter=',')
+
+connection = sqlite3.connect('project_data.db')
+cursor = connection.cursor()
+
+cursor.execute(
+		'''
+			SELECT Count(*), Month, Year FROM complaints
+			WHERE IsCyber = 1
+			GROUP BY Year, Month
+			ORDER BY Year ASC, Month ASC
+	    ''')
+
+cyber_rows = cursor.fetchall()
+
+
+cursor.execute(
+		'''
+			SELECT Count(*), Month, Year FROM complaints
+			WHERE IsCyber = 0
+			GROUP BY Year, Month
+			ORDER BY Year ASC, Month ASC
+	    ''')
+
+reg_rows = cursor.fetchall()
+
+for i in reg_rows:
+ 	for j in cyber_rows:
+
+ 		if str(list(i)[1:3]) == str(list(j)[1:3]):
+
+ 			new_date = str(str(list(i)[2])+str(list(i)[1]))
+ 			new_row = [new_date, i[0], j[0]]
+ 			data_writer.writerow(new_row)
+
+

### 2017-01-15 src/3_reporting_methods.py

@@ -1,0 +1,44 @@
+# Top agencies that were contacted
+import os
+import csv
+import sqlite3
+
+
+DATA_PATH  = "./data"
+OUT_PATH = "../plots"
+
+
+csv_file = open(os.path.join(OUT_PATH, 'top_agencies.csv'), "w")
+data_writer = csv.writer(csv_file,delimiter=',')
+
+connection = sqlite3.connect('project_data.db')
+cursor = connection.cursor()
+
+cursor.execute(
+		'''
+			SELECT Count(*) as A, Organization FROM complaints
+			WHERE IsCyber = 1
+			GROUP BY Organization
+			ORDER BY A Desc
+
+	    ''')
+
+cyber_rows = cursor.fetchall()
+
+cursor.execute(
+		'''
+			SELECT Count(*) as A, Organization FROM complaints
+			WHERE IsCyber = 0
+			GROUP BY Organization
+			ORDER BY A Desc
+	    ''')
+
+reg_rows = cursor.fetchall()
+
+for i in reg_rows:
+	for j in cyber_rows:
+
+		if list(i)[1] == list(j)[1]:
+			new_row = [list(i)[1], list(i)[0], list(j)[0]]
+			data_writer.writerow(new_row)
+

### 2017-01-15 src/dump_db.py

@@ -57,8 +57,9 @@ def add_ftc_data():
 	        	FraudDate DATE,
 	        	ReportingDate DATE,
 	        	IsCyber BOOLEAN,
-	        	Month TEXT,
-	        	Year TEXT)
+	        	Day INT,
+	        	Month INT,
+	        	Year INT)
 	    ''')
 
 		connection.commit()
@@ -76,16 +77,18 @@ def add_ftc_data():
 			  		FraudType = line['ProductCodeDesc']
 			  		FraudDate = line['InitialContactDate']
 			  		ReportingDate = line['AgencyContactDate']
-			  		IsCyber = is_cyber(ReportingMethod, FraudType)
+			  		IsCyber = is_cyber(ContactMethod, FraudType)
+			  		Day = ReportingDate.split("/")[1]
 			  		Month = ReportingDate.split("/")[0]
 			  		Year = ReportingDate.split("/")[2]
 
-			  		data = (Organization, CustomerZip, FraudZip, ContactMethod, SecContactMethod, FraudType, FraudDate, ReportingDate, IsCyber, Year, Month)
+			  		data = (Organization, CustomerZip, FraudZip, ContactMethod, SecContactMethod, FraudType, FraudDate, ReportingDate, IsCyber, Day, Month, Year)
 			  		cursor.execute("INSERT INTO complaints VALUES %s " % str(data))
 			  		count = count+1;
-			  	except:
+			  	except Exception as e:
+			  		print(e)
 			  		continue
-		print(count)
+
 
 def add_income_data():
 	cursor.execute(
@@ -157,6 +160,61 @@ def add_age_data():
 
 
 
+def add_college_data():
+	cursor.execute(
+	'''
+		CREATE TABLE education(
+			ZipCode TEXT PRIMARY KEY,
+			CollegePerc REAL)
+    ''')
+	
+	with open(os.path.join(DATA_PATH, 'college_data.csv')) as csvfile:
+		reader = csv.DictReader(csvfile)
+		for line in reader:
+			try:
+				ZipCode = line['ZIPCODE']
+				PercCollege = line['PERC'].split(" ")[0]
+
+				if len(ZipCode) > 0 and len(PercCollege):
+
+					data = (ZipCode, PercCollege)
+					cursor.execute("INSERT INTO education VALUES %s " % str(data))
+			except:
+				continue
+
+
+
+def add_race_data():
[…]

### 2017-01-15 src/scraper/college_scraper.py

@@ -1,0 +1,37 @@
+# Scrape college graduates percenteage from zipatlas
+import sys
+import bs4
+import requests
+import csv
+import time
+
+BASE_URL = "http://zipatlas.com/us/zip-code-comparison/percentage-college-graduates.htm"
+csv_file = open("college_data.csv", "w")
+data_writer = csv.writer(csv_file,delimiter=',')
+
+for i in range(1, 318):
+
+	if i == 1:
+		new_url = BASE_URL
+		r = requests.get(new_url)
+	else:
+		new = str(i)+".htm"
+		new_url = BASE_URL.replace("htm",new)
+		r = requests.get(new_url)
+
+	if r.status_code == 200:
+		print("new_page")
+		page_content = r.content
+
+		data = bs4.BeautifulSoup(page_content, "html.parser")
+		zip_data = data.find_all("td", { "class" : "report_data"})
+
+		for x in range(0,700,7):
+			result_arr = []
+			new_data = (zip_data[x:x+7])
+			
+			for j in new_data:
+				result_arr.append(j.text.replace(",", "."))
+			data_writer.writerow(result_arr)
+		time.sleep(5)
+		print(new_url)

### 2017-01-15 plots/reporting_methods.m
updated evaluation

@@ -5,6 +5,18 @@ x = [1,2];
 y = [33.35, 66.64; 82.18 17.81];
 
 figure;
-barh(x,y,'stacked'); % stacks values in each row together
-title('Stacked Style')
+b = barh(x,y,'stacked', 'r', 'EdgeColor',[0 0 0],'LineWidth',1.5, 'BarWidth', 0.5); % stacks values in each row together
+b(2).FaceColor = 'b';
+axis([0 100 0 3])
+set(gca, 'FontSize', 20)
+ylabel('Fraud Type Cyber Regular', 'FontSize', 20)
+set(gca,'yticklabel',{[]}) 
+xlabel('Percentage', 'FontSize', 20)
+legend('Online', 'Offline', 'Location','northeast', 'FontSize', 25)
+
+
+set(gcf, 'PaperPosition', [0 0 10 4]); %Position plot at left hand corner with width 5 and height 5.
+set(gcf, 'PaperSize', [10 4]); %Set the paper to have width 5 and height 5.
+%axis([0 128 0 280])
+saveas(gcf, 'reporting methods', 'pdf') %Save figure
 

### 2017-01-15 src/1_temporal_day.py

@@ -1,4 +1,4 @@
-# The main sripts that dumps all the datasets into the tables for querying
+# get aggregated frauds by day, more granular
 import os
 import csv
 import sqlite3

### 2017-01-15 src/2_temporal_month.py

@@ -1,4 +1,4 @@
-# The main sripts that dumps all the datasets into the tables for querying
+# get aggregated frauds by month
 import os
 import csv
 import sqlite3

### 2017-01-15 src/3_reporting_methods.py

@@ -1,14 +1,13 @@
-# Top agencies that were contacted
+# Get sorted list of agencies that were contacted to report fraud
 import os
 import csv
 import sqlite3
-
 
 DATA_PATH  = "./data"
 OUT_PATH = "../plots"
 
 
-csv_file = open(os.path.join(OUT_PATH, 'top_agencies.csv'), "w")
+csv_file = open(os.path.join(OUT_PATH, '3_reporting_methods.csv'), "w")
 data_writer = csv.writer(csv_file,delimiter=',')
 
 connection = sqlite3.connect('project_data.db')

### 2017-01-15 src/4_top_fraudsters.py
spell check, add top fraudster to Eval

@@ -7,7 +7,7 @@ DATA_PATH  = "./data"
 OUT_PATH = "../plots"
 
 
-csv_file = open(os.path.join(OUT_PATH, '3_reporting_methods.csv'), "w")
+csv_file = open(os.path.join(OUT_PATH, '4_top_fraudsters.csv'), "w")
 data_writer = csv.writer(csv_file,delimiter=',')
 
 connection = sqlite3.connect('project_data.db')
@@ -15,20 +15,23 @@ cursor = connection.cursor()
 
 cursor.execute(
 		'''
-			SELECT Count(*) as A, Organization FROM complaints
-			WHERE IsCyber = 1
-			GROUP BY Organization
-			ORDER BY A Desc
+			SELECT Count(*) as A, geodata.MSAName FROM geodata
+			INNER JOIN complaints ON  geodata.ZipCode == complaints.FraudZip
+			WHERE complaints.IsCyber = 1
+			GROUP BY geodata.MSAName
+			Order BY A DESC
 	    ''')
+
 
 cyber_rows = cursor.fetchall()
 
 cursor.execute(
 		'''
-			SELECT Count(*) as A, Organization FROM complaints
-			WHERE IsCyber = 0
-			GROUP BY Organization
-			ORDER BY A Desc
+			SELECT Count(*) as A, geodata.MSAName FROM geodata
+			INNER JOIN complaints ON  geodata.ZipCode == complaints.FraudZip
+			WHERE complaints.IsCyber = 0
+			GROUP BY geodata.MSAName
+			Order BY A DESC
 	    ''')
 
 reg_rows = cursor.fetchall()

### 2017-01-16 src/4_top_fraudsters.py
relatd work tewaks, distnace cdf

@@ -13,6 +13,8 @@ data_writer = csv.writer(csv_file,delimiter=',')
 connection = sqlite3.connect('project_data.db')
 cursor = connection.cursor()
 
+
+
 cursor.execute(
 		'''
 			SELECT Count(*) as A, geodata.MSAName FROM geodata
@@ -22,8 +24,9 @@ cursor.execute(
 			Order BY A DESC
 	    ''')
 
-
 cyber_rows = cursor.fetchall()
+
+
 
 cursor.execute(
 		'''

### 2017-01-16 src/5_zip_distances.py

@@ -1,0 +1,62 @@
+# Get Zipdode distacnes
+import os
+import csv
+import sqlite3
+import zipcode
+import geopy
+from geopy.distance import vincenty
+
+
+DATA_PATH  = "./data"
+OUT_PATH = "../plots"
+
+connection = sqlite3.connect('project_data.db')
+
+cursor = connection.cursor()
+
+# Get Cyber Distances 
+csv_file = open(os.path.join(OUT_PATH, '5_distances_cyber.csv'), "w")
+
+
+
+cursor.execute(
+		'''
+			SELECT FraudZip, CustomerZip FROM complaints
+			WHERE IsCyber = 1 AND FraudZip != '99999'
+	    ''')
+
+cyber_rows = cursor.fetchall()
+
+for x in cyber_rows:
+	f_zip = zipcode.isequal(list(x)[0])
+	c_zip = zipcode.isequal(list(x)[1])
+
+	if f_zip!= None and c_zip!= None:
+		f_cord = (f_zip.lat, f_zip.lon)
+		c_cord = (c_zip.lat, c_zip.lon)
+		csv_file.write(str(vincenty(f_cord, c_cord).miles)+"\n")
+
+
+# Get Regular Distances 
+csv_file = open(os.path.join(OUT_PATH, '5_distances_regular.csv'), "w")
+data_writer = csv.writer(csv_file,delimiter=',')
+
+
+cursor.execute(
+		'''
+			SELECT FraudZip, CustomerZip FROM complaints
+			WHERE IsCyber = 0 AND FraudZip != '99999'
+	    ''')
+
+cyber_rows = cursor.fetchall()
+
+for x in cyber_rows:
+	f_zip = zipcode.isequal(list(x)[0])
+	c_zip = zipcode.isequal(list(x)[1])
+
+	if f_zip!= None and c_zip!= None:
+		f_cord = (f_zip.lat, f_zip.lon)
+		c_cord = (c_zip.lat, c_zip.lon)
+		csv_file.write(str(vincenty(f_cord, c_cord).miles)+"\n")
+
+

### 2017-01-16 src/6_date_differences.py

@@ -1,0 +1,59 @@
+# Get Differences in Dates
+import os
+import csv
+import sqlite3
+from datetime import datetime
+
+
+DATA_PATH  = "./data"
+OUT_PATH = "../plots"
+
+connection = sqlite3.connect('project_data.db')
+
+cursor = connection.cursor()
+
+# Get Cyber Distances 
+csv_file = open(os.path.join(OUT_PATH, '5_distances_cyber.csv'), "w")
+
+
+cursor.execute(
+		'''
+			SELECT FraudZip, CustomerZip FROM complaints
+			WHERE IsCyber = 1 AND FraudZip != '99999'
+	    ''')
+
+cyber_rows = cursor.fetchall()
+
+for x in cyber_rows:
+	f_zip = zipcode.isequal(list(x)[0])
+	c_zip = zipcode.isequal(list(x)[1])
+
+	if f_zip!= None and c_zip!= None:
+		f_cord = (f_zip.lat, f_zip.lon)
+		c_cord = (c_zip.lat, c_zip.lon)
+		csv_file.write(str(vincenty(f_cord, c_cord).miles)+"\n")
+
+
+# Get Regular Distances 
+csv_file = open(os.path.join(OUT_PATH, '5_distances_regular.csv'), "w")
+data_writer = csv.writer(csv_file,delimiter=',')
+
+
+cursor.execute(
+		'''
+			SELECT FraudZip, CustomerZip FROM complaints
+			WHERE IsCyber = 0 AND FraudZip != '99999'
+	    ''')
+
+cyber_rows = cursor.fetchall()
+
+for x in cyber_rows:
+	f_zip = zipcode.isequal(list(x)[0])
+	c_zip = zipcode.isequal(list(x)[1])
+
+	if f_zip!= None and c_zip!= None:
+		f_cord = (f_zip.lat, f_zip.lon)
+		c_cord = (c_zip.lat, c_zip.lon)
+		csv_file.write(str(vincenty(f_cord, c_cord).miles)+"\n")
+
+

### 2017-01-16 src/4_top_fraudsters.py
almost there

@@ -14,12 +14,13 @@ connection = sqlite3.connect('project_data.db')
 cursor = connection.cursor()
 
 
-
 cursor.execute(
 		'''
-			SELECT Count(*) as A, geodata.MSAName FROM geodata
-			INNER JOIN complaints ON  geodata.ZipCode == complaints.FraudZip
-			WHERE complaints.IsCyber = 1
+			SELECT COUNT(*) as A, SUM(Tab.Population), geodata.MSAName FROM 
+				(SELECT complaints.FraudZip, populations.Population FROM complaints
+				INNER JOIN populations ON  populations.ZipCode == complaints.FraudZip
+				WHERE complaints.IsCyber = 1) Tab
+			INNER JOIN geodata ON geodata.ZipCode == Tab.FraudZip
 			GROUP BY geodata.MSAName
 			Order BY A DESC
 	    ''')
@@ -30,9 +31,11 @@ cyber_rows = cursor.fetchall()
 
 cursor.execute(
 		'''
-			SELECT Count(*) as A, geodata.MSAName FROM geodata
-			INNER JOIN complaints ON  geodata.ZipCode == complaints.FraudZip
-			WHERE complaints.IsCyber = 0
+			SELECT COUNT(*) as A, SUM(Tab.Population), geodata.MSAName FROM 
+				(SELECT complaints.FraudZip, populations.Population FROM complaints
+				INNER JOIN populations ON  populations.ZipCode == complaints.FraudZip
+				WHERE complaints.IsCyber = 0) Tab
+			INNER JOIN geodata ON geodata.ZipCode == Tab.FraudZip
 			GROUP BY geodata.MSAName
 			Order BY A DESC
 	    ''')
@@ -41,8 +44,7 @@ reg_rows = cursor.fetchall()
 
 for i in reg_rows:
 	for j in cyber_rows:
-
-		if list(i)[1] == list(j)[1]:
-			new_row = [list(i)[1], list(i)[0], list(j)[0]]
+		if list(i)[2] == list(j)[2]:
+			new_row = [list(i)[2], list(i)[0], list(i)[1], list(j)[0], list(i)[1],  float(list(i)[0])*1000/float(list(i)[1]), float(list(j)[0])*1000/float(list(j)[1])]
 			data_writer.writerow(new_row)
 

### 2017-01-16 src/6_date_differences.py

@@ -5,6 +5,14 @@ import sqlite3
 from datetime import datetime
 
 
+
+def days_between(d1, d2):
+# function obtained from
+#http://stackoverflow.com/questions/8419564/difference-between-two-dates
+    d1 = datetime.strptime(d1, "%m/%d/%y")
+    d2 = datetime.strptime(d2, "%m/%d/%y")
+    return abs((d2 - d1).days)
+
 DATA_PATH  = "./data"
 OUT_PATH = "../plots"
 
@@ -12,48 +20,76 @@ connection = sqlite3.connect('project_data.db')
 
 cursor = connection.cursor()
 
-# Get Cyber Distances 
-csv_file = open(os.path.join(OUT_PATH, '5_distances_cyber.csv'), "w")
+# Get Cyber Dates 
+csv_file = open(os.path.join(OUT_PATH, '6_dates_cyber.csv'), "w")
 
 
 cursor.execute(
 		'''
-			SELECT FraudZip, CustomerZip FROM complaints
-			WHERE IsCyber = 1 AND FraudZip != '99999'
+			SELECT FraudDate, ReportingDate FROM complaints
+			WHERE IsCyber = 1 AND FraudDate != 'NULL'
 	    ''')
 
 cyber_rows = cursor.fetchall()
 
 for x in cyber_rows:
-	f_zip = zipcode.isequal(list(x)[0])
-	c_zip = zipcode.isequal(list(x)[1])
-
-	if f_zip!= None and c_zip!= None:
-		f_cord = (f_zip.lat, f_zip.lon)
-		c_cord = (c_zip.lat, c_zip.lon)
-		csv_file.write(str(vincenty(f_cord, c_cord).miles)+"\n")
+	try:
+		if int(days_between(list(x)[0], list(x)[1])) < 366:
+			csv_file.write(str(days_between(list(x)[0], list(x)[1]))+"\n")  
+	except:
+		continue
 
 
-# Get Regular Distances 
-csv_file = open(os.path.join(OUT_PATH, '5_distances_regular.csv'), "w")
-data_writer = csv.writer(csv_file,delimiter=',')
-
+# Get Regular Dates 
+csv_file = open(os.path.join(OUT_PATH, '6_dates_regular.csv'), "w")
 
 cursor.execute(
 		'''
-			SELECT FraudZip, CustomerZip FROM complaints
[…]

### 2017-01-16 src/tmp.py

@@ -1,0 +1,52 @@
+# Get sorted list of agencies that were contacted to report fraud
+import os
+import csv
+import sqlite3
+
+DATA_PATH  = "./data"
+OUT_PATH = "../plots"
+
+
+csv_file = open(os.path.join(OUT_PATH, '7_tmp.csv'), "w")
+data_writer = csv.writer(csv_file,delimiter=',')
+
+connection = sqlite3.connect('project_data.db')
+cursor = connection.cursor()
+
+cursor.execute(
+		'''
+			SELECT COUNT(*) as A, SUM(Tab.Population), geodata.MSAName FROM 
+				(SELECT complaints.FraudZip, populations.Population FROM complaints
+				INNER JOIN populations ON  populations.ZipCode == complaints.FraudZip
+				WHERE complaints.IsCyber = 1) Tab
+			INNER JOIN geodata ON geodata.ZipCode == Tab.FraudZip
+			GROUP BY geodata.MSAName
+			Order BY A DESC
+	    ''')
+
+cyber_rows = cursor.fetchall()
+
+for x in cyber_rows:
+	print(x)
+# cursor.execute(
+# 		'''
+# 			SELECT COUNT(*) as A, SUM(Tab.Population), geodata.MSAName FROM 
+# 				(SELECT complaints.FraudZip, populations.Population FROM complaints
+# 				INNER JOIN populations ON  populations.ZipCode == complaints.FraudZip
+# 				WHERE complaints.IsCyber = 1) Tab
+# 			INNER JOIN geodata ON geodata.ZipCode == Tab.FraudZip
+# 			GROUP BY geodata.MSAName, Tab.Population
+# 			Order BY A DESC
+# 	    ''')
+
+# cyber_rows = cursor.fetchall()
+
+# reg_rows = cursor.fetchall()
+
+# for i in reg_rows:
+# 	for j in cyber_rows:
+
+# 		if list(i)[1] == list(j)[1]:
+# 			new_row = [list(i)[1], list(i)[0], list(j)[0]]
+# 			data_writer.writerow(new_row)
+

### 2017-01-17 plots/days_cdf.m
fraud trends, limitations

@@ -1,0 +1,25 @@
+
+% Days CDF
+load('6.mat')
+
+[f_cyber,x_cyber] = ecdf(cyber_6);
+[f_reg,x_reg] = ecdf(regular_6);
+
+figure;
+plot(x_cyber, f_cyber ,'r--', 'LineWidth', 2);
+hold on
+plot(x_reg, f_reg ,'b', 'LineWidth', 2);
+set(gca,'FontSize', 24)
+axis([0 300 0 1])
+axis square
+legend('Cyber','Regular', 'Location','southeast', 'FontSize', 24)
+
+grid on
+xlabel('Number of Days', 'FontSize', 24)
+ylabel('Distribution', 'FontSize', 24)
+
+set(gcf, 'PaperPosition', [0 0 7 6]); %Position plot at left hand corner with width 5 and height 5.
+set(gcf, 'PaperSize', [7 6]); %Set the paper to have width 5 and height 5.
+%axis([0 128 0 280])
+saveas(gcf, 'days', 'pdf') %Save figure
+% Reporting Dates CDF

### 2017-01-17 plots/distances_cdf.m

@@ -1,0 +1,54 @@
+
+
+
+figure;
+subplot(1,2,1)
+% Distances CDF
+load('6.mat')
+
+[f_cyber,x_cyber] = ecdf(cyber_6);
+[f_reg,x_reg] = ecdf(regular_6);
+
+
+plot(x_cyber, f_cyber ,'r--', 'LineWidth', 2);
+hold on
+plot(x_reg, f_reg ,'b', 'LineWidth', 2);
+set(gca,'FontSize', 24)
+axis([0 300 0 1])
+axis square
+legend('Cyber','Regular', 'Location','southeast', 'FontSize', 24)
+
+grid on
+xlabel('Number of Days', 'FontSize', 24)
+ylabel('Distribution', 'FontSize', 24)
+
+
+
+hold on
+% Distances CDF
+load('5.mat')
+
+[f_cyber,x_cyber] = ecdf(cyber_5);
+[f_reg,x_reg] = ecdf(regular_5);
+
+
+subplot(1,2,2)
+
+plot(x_cyber, f_cyber ,'r--', 'LineWidth', 2);
+hold on
+plot(x_reg, f_reg ,'b', 'LineWidth', 2);
+set(gca,'FontSize', 24)
+axis([0 3500 0 1])
+axis square
+legend('Cyber','Regular', 'Location','southeast', 'FontSize', 24)
+
+grid on
+xlabel('Distance (miles)', 'FontSize', 24)
+ylabel('Distribution', 'FontSize', 24)
+
+
+set(gcf, 'PaperPosition', [0 0 14 9]); %Position plot at left hand corner with width 5 and height 5.
+set(gcf, 'PaperSize', [14 9]); %Set the paper to have width 5 and height 5.
+%axis([0 128 0 280])
+saveas(gcf, 'dist_days', 'pdf') %Save figure
+% % Reporting Dates CDF

### 2017-01-17 plots/reg_vs_holiday.m

@@ -6,14 +6,19 @@ reg_h =sum(reg(349:369))
 cyb_n =sum(cyber(227:247))
 reg_n =sum(reg(227:247))
 
-y = [cyb_n reg_n; cyb_h reg_h;];
-b = bar(y, 'r', 'EdgeColor',[0 0 0],'LineWidth',1.5, 'BarWidth', 0.5)
-
-b(2).FaceColor = 'b';
-legend('Cyber','Regular', 'Location','northeast', 'FontSize', 25)
-set(gca,'FontSize', 11)
-set(gca,'xtick',[])
-set(gcf, 'PaperPosition', [0 0 10 6]); %Position plot at left hand corner with width 5 and height 5.
-set(gcf, 'PaperSize', [10 6]); %Set the paper to have width 5 and height 5.
-%axis([0 128 0 280])
-saveas(gcf, 'reg_vs_holiday', 'pdf') %Save figure
+% figure;[h,p] = ttest(___)
+% y = [ reg_h cyb_h ; reg_n cyb_n ;];
+% 
+% b = barh(y, 'b', 'EdgeColor',[0 0 0],'LineWidth',1.5, 'BarWidth', 0.5)
+% 
+% b(2).FaceColor = 'r';
+% legend('Regular','Cyber', 'Location','southeast', 'FontSize', 20)
+% xlabel('Number of Fraud Reports', 'FontSize', 20)
+% ylabel('    Holidays         Working Days', 'FontSize', 20)
+% 
+% set(gca,'yticklabel',{[]}) 
+% set(gca,'FontSize', 20)
+% set(gcf, 'PaperPosition', [0 0 10 6]); %Position plot at left hand corner with width 5 and height 5.
+% set(gcf, 'PaperSize', [10 6]); %Set the paper to have width 5 and height 5.
+% %axis([0 128 0 280])
+% saveas(gcf, 'reg_vs_holiday', 'pdf') %Save figure

### 2017-01-17 plots/ages.m
demographics plot

@@ -1,0 +1,60 @@
+% Load Ages
+clear all
+load('7.mat')
+
+% create bins 0-30 30-40 40-50 50 >
+cyber_bins = [0 0 0 0 0];
+
+reg_bins = [0 0 0 0 0];
+
+age_tot = [0 0 0 0 0];
+
+
+for n = 1:length(age)
+    
+    
+    if (age(n) <= 30)
+        cyber_bins(1) = cyber_bins(1) + cyber(n); reg_bins(1) = reg_bins(1) + reg(n);
+        age_tot(1) = age_tot(1)+1;
+    end
+    
+    if (age(n) > 30 && age(n) <= 40)
+        cyber_bins(2) = cyber_bins(2) + cyber(n); reg_bins(2) = reg_bins(2) + reg(n);
+        age_tot(2) = age_tot(2)+1;
+    end
+        
+    if (age(n) > 40 && age(n) <= 45)
+        cyber_bins(3) = cyber_bins(3) + cyber(n); reg_bins(3) = reg_bins(3) + reg(n);
+        age_tot(3) = age_tot(3)+1;
+    end 
+    
+    if (age(n) > 45 && age(n) <= 50)
+        cyber_bins(4) = cyber_bins(4) + cyber(n); reg_bins(4) = reg_bins(4) + reg(n);
+        age_tot(4) = age_tot(4)+1;
+    end 
+    
+    if (age(n) > 50)
+        cyber_bins(5) = cyber_bins(5) + cyber(n); reg_bins(5) = reg_bins(5) + reg(n);
+        age_tot(5) = age_tot(5)+1;
+    end    
+end
+
+r= reg_bins./age_tot
+c = cyber_bins./age_tot
+x = [c;r]'
+b = bar(x, 'r', 'EdgeColor',[0 0 0],'LineWidth',0.5, 'BarWidth', 0.5)
+b(2).FaceColor = 'b';
+
+
+
+axis([0.5 5.5 0 4])
+labels = {'0-30','30-40','40-45','46-50','50+'};
+set(gca, 'XTick', 1:5, 'XTickLabel', labels);
+set(gca,'FontSize', 20);
+xlabel({'Ages';' ';'(a)'}', 'FontSize', 23)
+
+
+ylabel({'Fraud Rate'}, 'FontSize', 23)
+
+
+

### 2017-01-17 plots/education.m

@@ -1,0 +1,59 @@
+% eduomes
+% Load edus
+clear all
+load('9.mat')
+
+% create bins 0-30 30-40 40-50 50 >
+cyber_bins = [0 0 0 0 0];
+
+reg_bins = [0 0 0 0 0];
+
+edu_tot = [0 0 0 0 0];
+
+
+for n = 1:length(edu)
+    
+    
+    if (edu(n) <= 10)
+        cyber_bins(1) = cyber_bins(1) + cyber(n); reg_bins(1) = reg_bins(1) + reg(n);
+        edu_tot(1) = edu_tot(1)+1;
+    end
+    
+    if (edu(n) > 10 && edu(n) <= 20)
+        cyber_bins(2) = cyber_bins(2) + cyber(n); reg_bins(2) = reg_bins(2) + reg(n);
+        edu_tot(2) = edu_tot(2)+1;
+    end
+        
+    if (edu(n) > 20 && edu(n) <= 50)
+        cyber_bins(3) = cyber_bins(3) + cyber(n); reg_bins(3) = reg_bins(3) + reg(n);
+        edu_tot(3) = edu_tot(3)+1;
+    end 
+    
+    if (edu(n) > 50 && edu(n) <= 70)
+        cyber_bins(4) = cyber_bins(4) + cyber(n); reg_bins(4) = reg_bins(4) + reg(n);
+        edu_tot(4) = edu_tot(4)+1;
+    end 
+    
+    if (edu(n) > 70)
+        cyber_bins(5) = cyber_bins(5) + cyber(n); reg_bins(5) = reg_bins(5) + reg(n);
+        edu_tot(5) = edu_tot(5)+1;
+    end    
+end
+
+r =reg_bins./edu_tot
+c= cyber_bins./edu_tot
+x = [c;r]'
+b = bar(x, 'r', 'EdgeColor',[0 0 0],'LineWidth',0.5, 'BarWidth', 0.5)
+b(2).FaceColor = 'b';
+
+
+
+
+axis([0.5 5.5 0 2.45])
+labels = {'0-10','10-20','20-50','50-70','70+'};
+set(gca, 'XTick', 1:5, 'XTickLabel', labels);
+set(gca,'FontSize', 20);
+xlabel({'College Education (%)';' ';'(c)'}', 'FontSize', 23)
+
+
+ylabel({'Fraud Rate'}, 'FontSize', 23)

### 2017-01-17 plots/incomes.m

@@ -1,0 +1,68 @@
+% incomes
+% Load incs
+clear all
+load('8.mat')
+
+% create bins 0-30 30-40 40-50 50 >
+cyber_bins = [0 0 0 0 0];
+
+reg_bins = [0 0 0 0 0];
+
+inc_tot = [0 0 0 0 0];
+
+
+for n = 1:length(inc)
+    
+    
+    if (inc(n) <= 30000)
+        cyber_bins(1) = cyber_bins(1) + cyber(n); reg_bins(1) = reg_bins(1) + reg(n);
+        inc_tot(1) = inc_tot(1)+1;
+    end
+    
+    if (inc(n) > 30000 && inc(n) <= 50000)
+        cyber_bins(2) = cyber_bins(2) + cyber(n); reg_bins(2) = reg_bins(2) + reg(n);
+        inc_tot(2) = inc_tot(2)+1;
+    end
+        
+    if (inc(n) > 50000 && inc(n) <= 70000)
+        cyber_bins(3) = cyber_bins(3) + cyber(n); reg_bins(3) = reg_bins(3) + reg(n);
+        inc_tot(3) = inc_tot(3)+1;
+    end 
+    
+    if (inc(n) > 70000 && inc(n) <= 90000)
+        cyber_bins(4) = cyber_bins(4) + cyber(n); reg_bins(4) = reg_bins(4) + reg(n);
+        inc_tot(4) = inc_tot(4)+1;
+    end 
+    
+    if (inc(n) > 90000)
+        cyber_bins(5) = cyber_bins(5) + cyber(n); reg_bins(5) = reg_bins(5) + reg(n);
+        inc_tot(5) = inc_tot(5)+1;
+    end    
+end
+
+
+r= reg_bins./inc_tot
+c = cyber_bins./inc_tot
+x = [c;r]'
+b = bar(x, 'r', 'EdgeColor',[0 0 0],'LineWidth',0.5, 'BarWidth', 0.5)
+b(2).FaceColor = 'b';
+
+
+
+
+axis([0.5 5.5 0 2.25])
+labels = {'0-30','30-50','50-70','70-90','90+'};
+set(gca, 'XTick', 1:5, 'XTickLabel', labels);
+set(gca,'FontSize', 20);
+xlabel({'Incomes (thousands)';' ';'(b)'}', 'FontSize', 23)
+
+
+ylabel({'Fraud Rate'}, 'FontSize', 23)
+
+
+
+
+
+
+
+

### 2017-01-17 plots/plot_bars.m

@@ -1,0 +1,16 @@
+close all
+figure;
+hold on
+subplot(2,2,1)
+ages;
+subplot(2,2,2)
+incomes;
+subplot(2,2,3)
+education;
+subplot(2,2,4)
+unemployment;
+set(gcf, 'PaperPosition', [0 0 14 9]); %Position plot at left hand corner with width 5 and height 5.
+set(gcf, 'PaperSize', [14 9]); %Set the paper to have width 5 and height 5.
+%axis([0 128 0 280])
+saveas(gcf, 'demographics', 'pdf') %Save figure
+% % Reporting Dates CDF

### 2017-01-17 plots/reg_vs_holiday.m

@@ -18,7 +18,6 @@ reg_n =sum(reg(227:247))
 % 
 % set(gca,'yticklabel',{[]}) 
 % set(gca,'FontSize', 20)
-% set(gcf, 'PaperPosition', [0 0 10 6]); %Position plot at left hand corner with width 5 and height 5.
-% set(gcf, 'PaperSize', [10 6]); %Set the paper to have width 5 and height 5.
-% %axis([0 128 0 280])
-% saveas(gcf, 'reg_vs_holiday', 'pdf') %Save figure
+set(gcf, 'PaperPosition', [0 0 10 7]); %Position plot at left hand corner with width 5 and height 5.
+set(gcf, 'PaperSize', [10 7]); %Set the paper to have width 5 and height 5.
+saveas(gcf, 'reg_vs_holiday', 'pdf') %Save figure

### 2017-01-17 plots/unemployment.m

@@ -1,0 +1,57 @@
+% unpomes
+% Load unps
+clear all
+load('10.mat')
+
+% create bins 0-30 30-40 40-50 50 >
+cyber_bins = [0 0 0 0 0];
+
+reg_bins = [0 0 0 0 0];
+
+unp_tot = [0 0 0 0 0];
+
+
+for n = 1:length(unp)
+    
+    
+    if (unp(n) <= 3)
+        cyber_bins(1) = cyber_bins(1) + cyber(n); reg_bins(1) = reg_bins(1) + reg(n);
+        unp_tot(1) = unp_tot(1)+1;
+    end
+    
+    if (unp(n) > 3 && unp(n) <= 5)
+        cyber_bins(2) = cyber_bins(2) + cyber(n); reg_bins(2) = reg_bins(2) + reg(n);
+        unp_tot(2) = unp_tot(2)+1;
+    end
+        
+    if (unp(n) > 5 && unp(n) <= 10)
+        cyber_bins(3) = cyber_bins(3) + cyber(n); reg_bins(3) = reg_bins(3) + reg(n);
+        unp_tot(3) = unp_tot(3)+1;
+    end 
+    
+    if (unp(n) > 10 && unp(n) <= 15)
+        cyber_bins(4) = cyber_bins(4) + cyber(n); reg_bins(4) = reg_bins(4) + reg(n);
+        unp_tot(4) = unp_tot(4)+1;
+    end 
+    
+    if (unp(n) > 15)
+        cyber_bins(5) = cyber_bins(5) + cyber(n); reg_bins(5) = reg_bins(5) + reg(n);
+        unp_tot(5) = unp_tot(5)+1;
+    end    
+end
+
+r =reg_bins./unp_tot
+c= cyber_bins./unp_tot
+x = [c;r]'
+b = bar(x, 'r', 'EdgeColor',[0 0 0],'LineWidth',0.5, 'BarWidth', 0.5)
+b(2).FaceColor = 'b';
+
+axis([0.5 5.5 0 5.5])
+labels = {'0-3','3-5','5-10','10-15','15+'};
+set(gca, 'XTick', 1:5, 'XTickLabel', labels);
+set(gca,'FontSize', 20);
+xlabel({'Unemployment Rate';' ';'(d)'}', 'FontSize', 23)
+
+ylabel({'Fraud Rate'}, 'FontSize', 23)
+legend('Cyber','Regular', 'Location','northeast', 'Orientation', 'horizontal')
+

### 2017-01-17 src/10_get_employment.py

@@ -1,0 +1,51 @@
+# Get sorted list of agencies that were contacted to report fraud
+import os
+import csv
+import sqlite3
+
+DATA_PATH  = "./data"
+OUT_PATH = "../plots"
+
+
+csv_file = open(os.path.join(OUT_PATH, '10_fraud_employment.csv'), "w")
+data_writer = csv.writer(csv_file,delimiter=',')
+
+connection = sqlite3.connect('project_data.db')
+cursor = connection.cursor()
+
+cursor.execute(
+		'''
+			SELECT CP.CustomerZip, CP.Crimes, CP.Population, employment.Unemployed FROM
+				(SELECT complaints.CustomerZip, COUNT(*) as Crimes, populations.Population FROM complaints
+				INNER JOIN populations ON  populations.ZipCode == complaints.CustomerZip
+				WHERE complaints.IsCyber = 1
+				GROUP BY complaints.CustomerZip) CP
+			INNER JOIN employment ON employment.ZipCode == CP.CustomerZip
+	    ''')
+
+
+cyber_rows = cursor.fetchall()
+
+cursor.execute(
+		'''
+			SELECT CP.CustomerZip, CP.Crimes, CP.Population, employment.Unemployed FROM
+				(SELECT complaints.CustomerZip, COUNT(*) as Crimes, populations.Population FROM complaints
+				INNER JOIN populations ON  populations.ZipCode == complaints.CustomerZip
+				WHERE complaints.IsCyber = 0
+				GROUP BY complaints.CustomerZip) CP
+			INNER JOIN employment ON employment.ZipCode == CP.CustomerZip
+	    ''')
+
+
+reg_rows = cursor.fetchall()
+
+
+for i in reg_rows:
+	for j in cyber_rows:
+		if list(i)[0] == list(j)[0]: #same zipcodes
+			try:
+
+				new_row = [list(i)[0], list(i)[1], list(i)[2], list(i)[3], float(list(i)[1])*1000/float(list(i)[2]), list(j)[1], list(j)[2], list(j)[3], float(list(j)[1])*1000/float(list(j)[2])]
+				data_writer.writerow(new_row)
+			except:
+				continue

### 2017-01-17 src/7_get_ages.py

@@ -1,0 +1,48 @@
+# Get sorted list of agencies that were contacted to report fraud
+import os
+import csv
+import sqlite3
+
+DATA_PATH  = "./data"
+OUT_PATH = "../plots"
+
+
+csv_file = open(os.path.join(OUT_PATH, '7_fraud_ages.csv'), "w")
+data_writer = csv.writer(csv_file,delimiter=',')
+
+connection = sqlite3.connect('project_data.db')
+cursor = connection.cursor()
+
+cursor.execute(
+		'''
+			SELECT CP.CustomerZip, CP.Crimes, CP.Population, ages.Age FROM
+				(SELECT complaints.CustomerZip, COUNT(*) as Crimes, populations.Population FROM complaints
+				INNER JOIN populations ON  populations.ZipCode == complaints.CustomerZip
+				WHERE complaints.IsCyber = 1
+				GROUP BY complaints.CustomerZip) CP
+			INNER JOIN ages ON ages.ZipCode == CP.CustomerZip
+	    ''')
+
+
+cyber_rows = cursor.fetchall()
+
+
+cursor.execute(
+		'''
+			SELECT CP.CustomerZip, CP.Crimes, CP.Population, ages.Age FROM
+				(SELECT complaints.CustomerZip, COUNT(*) as Crimes, populations.Population FROM complaints
+				INNER JOIN populations ON  populations.ZipCode == complaints.CustomerZip
+				WHERE complaints.IsCyber = 0
+				GROUP BY complaints.CustomerZip) CP
+			INNER JOIN ages ON ages.ZipCode == CP.CustomerZip
+	    ''')
+
+reg_rows = cursor.fetchall()
+
+
+for i in reg_rows:
+	for j in cyber_rows:
+		if list(i)[0] == list(j)[0]: #same zipcodes
+
+			new_row = [list(i)[0], list(i)[1], list(i)[2], list(i)[3], float(list(i)[1])*1000/float(list(i)[2]), list(j)[1], list(j)[2], list(j)[3], float(list(j)[1])*1000/float(list(j)[2])]
+			data_writer.writerow(new_row)

### 2017-01-17 src/8_get_incomes.py

@@ -1,0 +1,47 @@
+# Get sorted list of agencies that were contacted to report fraud
+import os
+import csv
+import sqlite3
+
+DATA_PATH  = "./data"
+OUT_PATH = "../plots"
+
+
+csv_file = open(os.path.join(OUT_PATH, '8_fraud_incomes.csv'), "w")
+data_writer = csv.writer(csv_file,delimiter=',')
+
+connection = sqlite3.connect('project_data.db')
+cursor = connection.cursor()
+
+cursor.execute(
+		'''
+			SELECT CP.CustomerZip, CP.Crimes, CP.Population, incomes.MedianIncome FROM
+				(SELECT complaints.CustomerZip, COUNT(*) as Crimes, populations.Population FROM complaints
+				INNER JOIN populations ON  populations.ZipCode == complaints.CustomerZip
+				WHERE complaints.IsCyber = 1
+				GROUP BY complaints.CustomerZip) CP
+			INNER JOIN incomes ON incomes.ZipCode == CP.CustomerZip
+	    ''')
+
+
+cyber_rows = cursor.fetchall()
+
+cursor.execute(
+		'''
+			SELECT CP.CustomerZip, CP.Crimes, CP.Population, incomes.MedianIncome FROM
+				(SELECT complaints.CustomerZip, COUNT(*) as Crimes, populations.Population FROM complaints
+				INNER JOIN populations ON  populations.ZipCode == complaints.CustomerZip
+				WHERE complaints.IsCyber = 0
+				GROUP BY complaints.CustomerZip) CP
+			INNER JOIN incomes ON incomes.ZipCode == CP.CustomerZip
+	    ''')
+
+reg_rows = cursor.fetchall()
+
+
+for i in reg_rows:
+	for j in cyber_rows:
+		if list(i)[0] == list(j)[0]: #same zipcodes
+
+			new_row = [list(i)[0], list(i)[1], list(i)[2], list(i)[3], float(list(i)[1])*1000/float(list(i)[2]), list(j)[1], list(j)[2], list(j)[3], float(list(j)[1])*1000/float(list(j)[2])]
+			data_writer.writerow(new_row)

### 2017-01-17 src/9_get_ecucation.py

@@ -1,0 +1,49 @@
+# Get sorted list of agencies that were contacted to report fraud
+import os
+import csv
+import sqlite3
+
+DATA_PATH  = "./data"
+OUT_PATH = "../plots"
+
+
+csv_file = open(os.path.join(OUT_PATH, '9_fraud_education.csv'), "w")
+data_writer = csv.writer(csv_file,delimiter=',')
+
+
+connection = sqlite3.connect('project_data.db')
+cursor = connection.cursor()
+
+
+cursor.execute(
+		'''
+			SELECT CP.CustomerZip, CP.Crimes, CP.Population, education.CollegePerc FROM
+				(SELECT complaints.CustomerZip, COUNT(*) as Crimes, populations.Population FROM complaints
+				INNER JOIN populations ON  populations.ZipCode == complaints.CustomerZip
+				WHERE complaints.IsCyber = 1
+				GROUP BY complaints.CustomerZip) CP
+			INNER JOIN education ON education.ZipCode == CP.CustomerZip
+	    ''')
+
+
+cyber_rows = cursor.fetchall()
+
+cursor.execute(
+		'''
+			SELECT CP.CustomerZip, CP.Crimes, CP.Population, education.CollegePerc FROM
+				(SELECT complaints.CustomerZip, COUNT(*) as Crimes, populations.Population FROM complaints
+				INNER JOIN populations ON  populations.ZipCode == complaints.CustomerZip
+				WHERE complaints.IsCyber = 0
+				GROUP BY complaints.CustomerZip) CP
+			INNER JOIN education ON education.ZipCode == CP.CustomerZip
+	    ''')
+
+reg_rows = cursor.fetchall()
+
+
+for i in reg_rows:
+	for j in cyber_rows:
+		if list(i)[0] == list(j)[0]: #same zipcodes
+
+			new_row = [list(i)[0], list(i)[1], list(i)[2], list(i)[3], float(list(i)[1])*1000/float(list(i)[2]), list(j)[1], list(j)[2], list(j)[3], float(list(j)[1])*1000/float(list(j)[2])]
+			data_writer.writerow(new_row)

### 2017-01-17 src/dump_db.py

@@ -17,6 +17,8 @@ TRUE_CYBERCRIMES = set(['Spyware\Adware\Malware', 'Internet Information Services
 						 'Internet Web Site Design\Promotion', 'Social Networking Service'])
 
 
+
+
 connection = sqlite3.connect('project_data.db')
 cursor = connection.cursor()
 
@@ -241,7 +243,32 @@ def add_geo_data():
 		  		cursor.execute("INSERT INTO geodata VALUES %s " % str(data))
 
 
+
+def add_employment_data():
+	cursor.execute(
+	'''
+		CREATE TABLE employment(
+			ZipCode TEXT PRIMARY KEY,
+			Unemployed REAL)
+    ''')
+
+	connection.commit()
+
+	with open(os.path.join(DATA_PATH, 'employment_data.csv')) as csvfile:
+	  	reader = csv.DictReader(csvfile)
+	  	for line in reader:
+
+	  		ZipCode = line['GEO.display-label'].split(" ")[1]
+	  		Unemployed = line['HC04_EST_VC01']
+
+	  		if len(Unemployed) > 0 and Unemployed != '-':
+		  		data = (ZipCode, Unemployed)
+		  		cursor.execute("INSERT INTO employment VALUES %s " % str(data))
+
+
+
 def main():
+	add_employment_data()
 	add_college_data()
 	add_race_data()
 	add_geo_data()

### 2017-01-17 src/tmp.py

@@ -13,6 +13,9 @@ data_writer = csv.writer(csv_file,delimiter=',')
 connection = sqlite3.connect('project_data.db')
 cursor = connection.cursor()
 
+
+
+
 cursor.execute(
 		'''
 			SELECT COUNT(*) as A, SUM(Tab.Population), geodata.MSAName FROM 
@@ -28,25 +31,24 @@ cyber_rows = cursor.fetchall()
 
 for x in cyber_rows:
 	print(x)
-# cursor.execute(
-# 		'''
-# 			SELECT COUNT(*) as A, SUM(Tab.Population), geodata.MSAName FROM 
-# 				(SELECT complaints.FraudZip, populations.Population FROM complaints
-# 				INNER JOIN populations ON  populations.ZipCode == complaints.FraudZip
-# 				WHERE complaints.IsCyber = 1) Tab
-# 			INNER JOIN geodata ON geodata.ZipCode == Tab.FraudZip
-# 			GROUP BY geodata.MSAName, Tab.Population
-# 			Order BY A DESC
-# 	    ''')
 
-# cyber_rows = cursor.fetchall()
 
-# reg_rows = cursor.fetchall()
 
-# for i in reg_rows:
-# 	for j in cyber_rows:
+Zipcode, Crime Count, Population, Median Age
 
-# 		if list(i)[1] == list(j)[1]:
-# 			new_row = [list(i)[1], list(i)[0], list(j)[0]]
-# 			data_writer.writerow(new_row)
 
+cursor.execute(
+		'''
+			SELECT  age.ZipCode, SUM(Tab.Population), geodata.MSAName FROM 
+				
+
+				(SELECT complaints.FraudZip, COUNT(*), populations.Population FROM complaints
+				INNER JOIN populations ON  populations.ZipCode == complaints.FraudZip
+				WHERE complaints.IsCyber = 1) complaint_pop
+
+
+
+			INNER JOIN geodata ON geodata.ZipCode == Tab.FraudZip
+			GROUP BY geodata.MSAName
+			Order BY A DESC
+	    ''')

### 2017-01-17 plots/ages.m
more coffee

@@ -54,7 +54,7 @@ set(gca,'FontSize', 20);
 xlabel({'Ages';' ';'(a)'}', 'FontSize', 23)
 
 
-ylabel({'Fraud Rate'}, 'FontSize', 23)
+ylabel({'Complaint Rate'}, 'FontSize', 23)
 
 
 

### 2017-01-17 plots/blacks.m

@@ -1,0 +1,31 @@
+clc
+close all
+prop = []
+
+
+cyber_dots = []
+reg_dots = []
+
+
+cur = data(1);
+temp_c = [cyber(1)];
+temp_r = [reg(1)];
+
+
+for n = 2:length(data)
+    
+    if (data(n) == cur)
+        temp_c = [temp_c cyber(n)];
+        temp_r = [temp_r reg(n)];
+    else
+        prop = [prop data(n-1)]
+        cyber_dots = [cyber_dots mean(temp_c)];
+        reg_dots = [reg_dots mean(temp_r)];
+        
+        temp_c = [cyber(n)];
+        temp_r = [cyber(n)];
+        cur = data(n);
+    end
+end
+
+scatter(prop, cyber_dots,'*')

### 2017-01-17 plots/education.m

@@ -56,4 +56,4 @@ set(gca,'FontSize', 20);
 xlabel({'College Education (%)';' ';'(c)'}', 'FontSize', 23)
 
 
-ylabel({'Fraud Rate'}, 'FontSize', 23)
+ylabel({'Complaint Rate'}, 'FontSize', 23)

### 2017-01-17 plots/incomes.m

@@ -57,7 +57,7 @@ set(gca,'FontSize', 20);
 xlabel({'Incomes (thousands)';' ';'(b)'}', 'FontSize', 23)
 
 
-ylabel({'Fraud Rate'}, 'FontSize', 23)
+ylabel({'Complaint Rate'}, 'FontSize', 23)
 
 
 

### 2017-01-17 plots/reg_vs_holiday.m

@@ -6,18 +6,18 @@ reg_h =sum(reg(349:369))
 cyb_n =sum(cyber(227:247))
 reg_n =sum(reg(227:247))
 
-% figure;[h,p] = ttest(___)
-% y = [ reg_h cyb_h ; reg_n cyb_n ;];
+y = [  cyb_h reg_h;  cyb_n reg_n;];
 % 
-% b = barh(y, 'b', 'EdgeColor',[0 0 0],'LineWidth',1.5, 'BarWidth', 0.5)
+b = barh(y, 'r', 'EdgeColor',[0 0 0],'LineWidth',1.5, 'BarWidth', 0.5)
 % 
-% b(2).FaceColor = 'r';
-% legend('Regular','Cyber', 'Location','southeast', 'FontSize', 20)
-% xlabel('Number of Fraud Reports', 'FontSize', 20)
-% ylabel('    Holidays         Working Days', 'FontSize', 20)
+b(2).FaceColor = 'b';
+
+legend('Cyber','Regular', 'Location','southeast', 'FontSize', 20)
+xlabel('Number of Fraud Reports', 'FontSize', 20)
+ylabel(' Holiday         Working', 'FontSize', 20)
 % 
-% set(gca,'yticklabel',{[]}) 
-% set(gca,'FontSize', 20)
+set(gca,'yticklabel',{[]}) 
+set(gca,'FontSize', 20)
 set(gcf, 'PaperPosition', [0 0 10 7]); %Position plot at left hand corner with width 5 and height 5.
 set(gcf, 'PaperSize', [10 7]); %Set the paper to have width 5 and height 5.
 saveas(gcf, 'reg_vs_holiday', 'pdf') %Save figure

### 2017-01-17 plots/unemployment.m

@@ -52,6 +52,7 @@ set(gca, 'XTick', 1:5, 'XTickLabel', labels);
 set(gca,'FontSize', 20);
 xlabel({'Unemployment Rate';' ';'(d)'}', 'FontSize', 23)
 
-ylabel({'Fraud Rate'}, 'FontSize', 23)
+ylabel({'Complaint Rate'}, 'FontSize', 23)
+
 legend('Cyber','Regular', 'Location','northeast', 'Orientation', 'horizontal')
 

### 2017-01-17 src/10_get_employment.py

@@ -34,7 +34,7 @@ cursor.execute(
 				WHERE complaints.IsCyber = 0
 				GROUP BY complaints.CustomerZip) CP
 			INNER JOIN employment ON employment.ZipCode == CP.CustomerZip
-	    ''')
+	    ''')Figure \ref{demographics} 
 
 
 reg_rows = cursor.fetchall()

### 2017-01-17 src/11_get_races.py

@@ -1,0 +1,48 @@
+# Get sorted list of agencies that were contacted to report fraud
+import os
+import csv
+import sqlite3
+
+DATA_PATH  = "./data"
+OUT_PATH = "../plots"
+
+
+
+csv_file = open(os.path.join(OUT_PATH, '11_fraud_races.csv'), "w")
+data_writer = csv.writer(csv_file,delimiter=',')
+
+
+connection = sqlite3.connect('project_data.db')
+cursor = connection.cursor()
+
+
+cursor.execute(
+		'''
+			SELECT CP.CustomerZip, CP.Crimes, CP.Population, races.PercWhite, races.PercBlack, races.PercAsian, races.PercLatin  FROM
+				(SELECT complaints.CustomerZip, COUNT(*) as Crimes, populations.Population FROM complaints
+				INNER JOIN populations ON  populations.ZipCode == complaints.CustomerZip
+				WHERE complaints.IsCyber = 1
+				GROUP BY complaints.CustomerZip) CP
+			INNER JOIN races ON races.ZipCode == CP.CustomerZip
+	    ''')
+
+cyber_rows = cursor.fetchall()
+cursor.execute(
+		'''
+			SELECT CP.CustomerZip, CP.Crimes, CP.Population, races.PercWhite, races.PercBlack, races.PercAsian, races.PercLatin  FROM
+				(SELECT complaints.CustomerZip, COUNT(*) as Crimes, populations.Population FROM complaints
+				INNER JOIN populations ON  populations.ZipCode == complaints.CustomerZip
+				WHERE complaints.IsCyber = 0
+				GROUP BY complaints.CustomerZip) CP
+			INNER JOIN races ON races.ZipCode == CP.CustomerZip
+	    ''')
+
+reg_rows = cursor.fetchall()
+for i in reg_rows:
+	for j in cyber_rows:
+		if list(i)[0] == list(j)[0]: #same zipcodes
+			try:
+				new_row = [list(i)[0], list(i)[1], list(i)[2], float(list(i)[1])*1000/float(list(i)[2]), float(list(j)[1])*1000/float(list(j)[2]), list(i)[3], list(i)[4], list(i)[5], list(i)[6]]
+				data_writer.writerow(new_row)
+			except:
+				continue

### 2017-01-17 src/12_get_all.py

@@ -1,0 +1,45 @@
+
+
+
+# Get sorted list of agencies that were contacted to report fraud
+import os
+import csv
+import sqlite3
+
+DATA_PATH  = "./data"
+OUT_PATH = "../plots"
+
+
+
+csv_file = open(os.path.join(OUT_PATH, '12_all_cyber.csv'), "w")
+data_writer = csv.writer(csv_file,delimiter=',')
+
+
+connection = sqlite3.connect('project_data.db')
+cursor = connection.cursor()
+
+cursor.execute(
+		'''
+			SELECT complaints.CustomerZip, COUNT(*) as A, populations.Population, ages.Age, incomes.MedianIncome, education.CollegePerc, employment.Unemployed, races.PercWhite, races.PercBlack, races.PercAsian, races.PercLatin 
+			FROM complaints 
+				JOIN populations 
+					ON populations.ZipCode = complaints.CustomerZip
+				JOIN races 
+					ON races.ZipCode = complaints.CustomerZip
+				JOIN ages 
+					ON ages.ZipCode = complaints.CustomerZip
+				JOIN incomes 
+					ON ages.ZipCode = complaints.CustomerZip
+				JOIN education 
+					ON education.ZipCode = complaints.CustomerZip
+				JOIN employment 
+					ON education.ZipCode = complaints.CustomerZip	
+			WHERE complaints.IsCyber = 1
+			GROUP BY complaints.CustomerZip
+	    ''')
+
+cyber_rows = cursor.fetchall()
+
+for i in cyber_rows:
+	data_writer.writerow(i)
+

### 2017-01-17 src/dump_db.py

@@ -186,7 +186,7 @@ def add_college_data():
 
 
 
-def add_race_data():
+def `():
 	cursor.execute(
 	'''
 		CREATE TABLE races(

### 2017-01-17 src/12_get_all.py
rectified citations

@@ -41,5 +41,5 @@ cursor.execute(
 cyber_rows = cursor.fetchall()
 
 for i in cyber_rows:
-	data_writer.writerow(i)
+	data_writer.writerow(list(i))
 

### 2017-01-17 plots/education.m
evaluation completed

@@ -29,12 +29,12 @@ for n = 1:length(edu)
         edu_tot(3) = edu_tot(3)+1;
     end 
     
-    if (edu(n) > 50 && edu(n) <= 70)
+    if (edu(n) > 50 && edu(n) <= 90)
         cyber_bins(4) = cyber_bins(4) + cyber(n); reg_bins(4) = reg_bins(4) + reg(n);
         edu_tot(4) = edu_tot(4)+1;
     end 
     
-    if (edu(n) > 70)
+    if (edu(n) > 90)
         cyber_bins(5) = cyber_bins(5) + cyber(n); reg_bins(5) = reg_bins(5) + reg(n);
         edu_tot(5) = edu_tot(5)+1;
     end    
@@ -48,8 +48,7 @@ b(2).FaceColor = 'b';
 
 
 
-
-axis([0.5 5.5 0 2.45])
+axis([0.5 5.5 0 3.5])
 labels = {'0-10','10-20','20-50','50-70','70+'};
 set(gca, 'XTick', 1:5, 'XTickLabel', labels);
 set(gca,'FontSize', 20);

### 2017-01-17 plots/regression_calc.m

@@ -1,0 +1,39 @@
+Y = double(reg_ds(:,2:end));
+[n,d] = size(Y);
+x = reg_ds.reg;
+
+% figure;
+% regions = reg_ds.Properties.VarNames(2:end);
+% plot(x,Y,'x')
+% legend(regions,'Location','NorthWest')
+
+X = cell(n,1);
+for i=1:n
+		X{i} = [eye(d) repmat(x(i),d,1)];
+end
+
+[beta,Sigma] = mvregress(X,Y);
+
+
+B = [beta(1:d)';repmat(beta(end),1,d)];
+
+
+xx = linspace(.5,100000)';
+
+fits = [ones(size(xx)),xx]*B;
+% 
+figure;
+h = plot(xx,fits,'-');
+% 
+% 
+% 
+% for i = 1:d
+% 	set(h(d+i),'color',get(h(i),'color'));
+% end
+% legend(regions,'Location','NorthWest');
+
+
+
+
+
+

### 2017-01-17 plots/unemployment.m

@@ -50,7 +50,7 @@ axis([0.5 5.5 0 5.5])
 labels = {'0-3','3-5','5-10','10-15','15+'};
 set(gca, 'XTick', 1:5, 'XTickLabel', labels);
 set(gca,'FontSize', 20);
-xlabel({'Unemployment Rate';' ';'(d)'}', 'FontSize', 23)
+xlabel({'Unemployment Rate (%)';' ';'(d)'}', 'FontSize', 23)
 
 ylabel({'Complaint Rate'}, 'FontSize', 23)
 

### 2017-01-17 plots/whites.m

@@ -1,0 +1,32 @@
+clc
+close all
+prop = []
+
+cyber_dots = []
+reg_dots = []
+
+cur = data(1);
+temp_c = [cyber(1)];
+temp_r = [reg(1)];
+
+
+for n = 2:length(data)
+    
+    if (data(n) == cur)
+        temp_c = [temp_c cyber(n)];
+        temp_r = [temp_r reg(n)];
+    else
+        prop = [prop data(n-1)];
+        cyber_dots = [cyber_dots mean(temp_c)];
+        reg_dots = [reg_dots mean(temp_r)];
+        
+        temp_c = [cyber(n)];
+        temp_r = [cyber(n)];
+        cur = data(n);
+    end
+end
+
+scatter(prop, cyber_dots,'*')
+hold on
+lsline
+scatter(prop, reg_dots,'*','r')

### 2017-01-17 src/9_get_ecucation.py

@@ -25,8 +25,8 @@ cursor.execute(
 			INNER JOIN education ON education.ZipCode == CP.CustomerZip
 	    ''')
 
-
 cyber_rows = cursor.fetchall()
+print(len(cyber_rows))
 
 cursor.execute(
 		'''
@@ -44,6 +44,8 @@ reg_rows = cursor.fetchall()
 for i in reg_rows:
 	for j in cyber_rows:
 		if list(i)[0] == list(j)[0]: #same zipcodes
-
-			new_row = [list(i)[0], list(i)[1], list(i)[2], list(i)[3], float(list(i)[1])*1000/float(list(i)[2]), list(j)[1], list(j)[2], list(j)[3], float(list(j)[1])*1000/float(list(j)[2])]
-			data_writer.writerow(new_row)
+			try:
+				new_row = [list(i)[0], list(i)[1], list(i)[2], list(i)[3], float(list(i)[1])*1000/float(list(i)[2]), list(j)[1], list(j)[2], list(j)[3], float(list(j)[1])*1000/float(list(j)[2])]
+				data_writer.writerow(new_row)
+			except:
+				aaaa=1

### 2017-01-17 src/run_regression.py

@@ -1,0 +1,15 @@
+
+from datalib import *
+import pandas
+import statsmodels.formula.api as sm
+import os
+
+# crime_1000,pop,income,perc_white,perc_black,perc_asian
+OUT_PATH = "../plots"
+
+
+if __name__=='__main__':
+
+	data = pandas.read_csv(os.path.join(OUT_PATH, 'python_reg_regression.csv'))
+	model = sm.ols(formula='reg ~ + age + income + college + unemp + white + black + asian + hisp + pop', data=data).fit()
+	print(model.summary())

### 2017-01-18 paper/paper.tex
no more paper in the repo

@@
 
+\usepackage{tabularx}
+\usepackage{lipsum}
+\usepackage{blindtext}
+\usepackage{graphicx}
+\usepackage{url}
+\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
+
+\newcommand{\ck}[1]{\textcolor{red}{#1}}
+
+\newcolumntype{K}[1]{>{\centering\arraybackslash}p{#1}}
+
 % correct bad hyphenation here
@@
 \begin{document}
-%
-% paper title
-% Titles are generally capitalized except for words such as a, an, and, as,
-% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
-% not capitalized unless they are the first or last word of the title.
-% Linebreaks \\ can be used within to get better formatting as desired.
-% Do not put math or special symbols in the title.
-\title{Cyber vs Regular: Understanding the State of Consumer Fraud in America
-}
+
+\title{Old is Still Gold: A Comparison of Cyber and Regular Consumer Fraud in The United States}
 
 % author names and affiliations
-% use a multiple column layout for up to three different
-% affiliations
-\author{\IEEEauthorblockN{Mohammad Taha Khan and
-Chris Kanich}
-\IEEEauthorblockA{Department of Computer Science, University of Illinois at Chicago\\
-taha@cs.uic.edu, ckanich@uic.edu}}
-
-% conference papers do not typically use \thanks and this command
-% is locked out in conference mode. If really needed, such as for
-% the acknowledgment of grants, issue a \IEEEoverridecommandlockouts
-% after \documentclass
-
-% for over three affiliations, or if they all won't fit within the width
-% of the page, use this alternative format:
-% 
-%\author{\IEEEauthorblockN{Michael Shell\IEEEauthorrefmark{1},
-%Homer Simpson\IEEEauthorrefmark{2},
-%James Kirk\IEEEauthorrefmark{3}, 
-%Montgomery Scott\IEEEauthorrefmark{3} and
-%Eldon Tyrell\IEEEauthorrefmark{4}}
-%\IEEEauthorblockA{\IEEEauthorrefmark{1}School of Electrical and Computer Engineering\\
-%Georgia Institute of Technology,
-%Atlanta, Georgia 30332--0250\\ Email: see http://www.michaelshell.org/contact.html}
-%\IEEEauthorblockA{\IEEEauthorrefmark{2}Twentieth Century Fox, Springfield, USA\\
-%Email: homer@thesimpsons.com}
-%\IEEEauthorblockA{\IEEEauthorrefmark{3}Starfleet Academy, San Francisco, California 96678-2391\\
-%Telephone: (800) 555--1212, Fax: (888) 555--1212}
-%\IEEEauthorblockA{\IEEEauthorrefmark{4}Tyrell Inc., 123 Replicant Street, Los Angeles, California 90210--4321}}
-
-% use for special paper notices
-%\IEEEspecialpapernotice{(Invited Paper)}
+%\author{\IEEEauthorblockN{Mohammad Taha Khan and Chris Kanich}
+%\IEEEauthorblockA{Department of Computer Science, University of Illinois at Chicago\\taha@cs.uic.edu, ckanich@uic.edu}}
 
@@
 \begin{abstract}
-The abstract goes here.
+
+While cybercrime is a relatively recent human invention, fraudulent activity has a much longer history.
+This paper investigates the differences in fraud reporting and targeting among United States based consumers by comparing fraudulent activity mediated by the Internet, with traditional forms of fraud.
+We find that \ck{ADD QUICK AND EASY CONCLUSIONS HERE}.
+
 \end{abstract}
 
-% no keywords
+\section{Introduction}
 
-% For peer review papers, you can put extra information on the cover
-% page as needed:
-% \ifCLASSOPTIONpeerreview
-% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
-% \fi
-%
-% For peerreview papers, this IEEEtran command inserts a page break and
-% creates the second title. It will be ignored for other modes.
-\IEEEpeerreviewmaketitle
+In the United States, a total of more that 25 million people are victims of frauds \ck{per year?} \cite{anderson2013consumer}.
+These deceptive scams are a major cause of economic damages to users, not to mention the added externalities of wasted time and stress.
+These illicit practices have been a part of the underground economy for a while.
+Initially individuals were tricked by scam calls, mail or in-person fraudsters, however, the rise of the Internet has provided fraudulent entities with a more streamlined exposure to the overall population.
+A  survey report from 2014 indicated that 47\% of Americans had been victims of an online identity theft.
+Another recent report released by the  Federal Trade Commission (FTC) revealed that debt collection, identity theft, and impostor scams contribute towards 56\% of the total frauds complaints in 2015 \cite{ftcpress2016} .
+With the number of Internet users on the rise, the number of cyber frauds is likely to increase over the next couple of years \cite{perharassment}.
+To deal with the increasing trend, the Federal Bureau of Investigation (FBI), alongside the FTC, has established a similar complaint portal known as the IC3, for the collection of specifically Internet-based fraudulent practices \cite{fbiic3}.
+This emerging trend of deceptive practices necessitates their study in order to evaluate and mitigate the harm caused to victims individuals.
 
-\section{Introduction}
-the main contributions:
-Understanding the differences in the  nature of cyber and regular frauds in the United States.
-Exploring if certain demographics are more succeptible to cybercrime
-Suggesting improvements that might be the right way to create more awareness annd campaings.
+This paper evaluates the nature of consumer fraud in the United States.
+Our work provides a comparison between cyber and traditional, non-cyber frauds.
+We categorize cyber frauds as all those deceptive practices that victimize users online, while regular ones comprise of frauds that target individuals over the phone, with mail, or in-person.
+While we understand that cyber frauds are a major focus of today's research, our comparison based approach allows us to better understand how they differ from conventional frauds.
+It also enables us to independently evaluate trends in regular frauds and to see whether fraudsters are adopting online mechanisms to target more individuals.
+This combined analysis can enable strategic suggestions to develop better fraud reduction methodologies.
 
-Fraud and and deceptive practices have been around since the establishment of
+To evaluate fraud trends, we use the FTC's Consumer Sentinel database, a dataset of complaints from the year 2013 and 2014.
+We also collect demographic information from the US Census Bureau \cite{uscensus}.
+In addition to data collection, we devise a calibration methodology to identify and separate cyber frauds from non-cyber in the complaint dataset.
 
-The FTC and the FBI
+Our work provides three main contributions.
+First, we evaluate the distinctive trends prevalent in cyber and regular frauds in the dataset.
+This encompasses their reporting numbers and methods.
+The nature of frauds which are more common in each specific category and the insights on the fraudsters who carry out these specific deceptive activities.
+Secondly, we look at ethnic, age, education and employment demographics in each specific category and evaluate if certain individuals are more likely to report crimes.
+Finally, based on our findings we provide suggestive measures that can be taken into account by regulatory agencies to reduce the overall fraud in the United States.
 
-According to a recent FTC survey report\cite{ftcfraud} shows that Intenet fraud had doubled within the past 6 years and now is the top most source of frauds within the the US.
+The rest of the paper is structured as follows, section \ref{related} provides a comprehensive overview of the relevant work.
+In section \ref{data-cal}, we elaborate features of the datasets used in our analysis along with a description of our calibration methodology.
+Section \ref{eval} summarizes our findings from the data followed by our suggestions to regulatory agencies in \ref{discussion}.
+We conclude our work in section \ref{conclusion} and discuss avenues of future research.
 
-Explain regualr and cyber fraud... dive details in categotization
+\section{Related Work}\label{related}
 
-\section{Related Work}
+\begin{table*}[h]
+\noindent
+\centering
+\begin{tabular}{K{0.18\linewidth}|p{0.72\linewidth}}
+\hline
+\multicolumn{1}{c}{\bfseries Data Field} & \multicolumn{1}{c}{\bfseries Field Description}
+\\ 
+\hline
+\hline
+Agency Name & The complaint collection agencies associated with the FTC.\\
+\hline
+Zip code Information & The zip code of the victim and the fraudulent entity.\\
+%This provided us with low level granularity for analysis, however, the latter was only available for a subset of the complaints\\
+\hline
+Contact Method & The primary channel used by the fraudulent entity to contact the victim e.g. Internet, phone, mail.\\
+\hline
+Fraud Description & A description of nature the fraud, and its type e.g. credit card, fake product, debt collection.\\
+\hline
+Fraud \&
+ Reporting Date & The dates when the fraud initially occurred and the date on which is was reported.
+\\
+\hline
+\end{tabular}
+\vspace{8pt}
+\caption{The description of the data fields that were primarily used in the for data calibration and analysis}\label{ftcdata}
+\vspace{-20pt}
+\end{table*}
 
-As our work evaluates both cyber as well as regular frauds, we provide related work that encompas both of these categories.
-However, we elaborate more on recent research that focuses on cyber frauds due to the increased Internet usage trends for sensitive activities leading to more individuals being vicitms of online frauds \cite{ftcfraud}.
-Before the Internet became a primarey source of economic and social acticity, resreaches measured \cite{ukphone} and developed techniques based on statisitical models \cite{creditfraud, phoenfraudnn, phonefraudstat} to detect phone and credit card based frauds.
-In the past few years, most research has shifted focus towards cyber activity \cite{databreach, playingfield, fraudfinance, cybertrends} due to its high potential for harm.
+As our work evaluates both cyber as well as regular frauds, we provide related work that encompasses both of these categories.
+However, we elaborate more on recent research which focuses on cyber frauds as more individuals are victims of these crimes \cite{anderson2013consumer} due to the increased Internet usage trends for sensitive activities.
+Before the Internet became a primary hub of economic and social activity, researchers measured \cite{clarke2001controlling} and developed techniques based on statistical models \cite{brause1999neural, moreau1997detection, bolton2002statistical, snyder2015no} to detect phone and credit card based frauds.
+In the past few years,  research evaluations have shifted focus towards cyber activity \cite{ablon2016consumer, piper2002, ionescu2011fraud, howard2007cyber} due to its high rate and the increased potential for harm.
 
-Even though, term \emph{"cyber"} is usually associated with Computer Science, due to its recent socio-economic impact, reseachers in Economics, Law and Finance have also explored for solutions to this problem by incorporating methodologies specific to their areas.
+Even though term \emph{"cyber fraud"} is usually associated with Computer Science, its recent socio-economic impact has motivated researchers in Economics, Law, and Finance to explore solutions by incorporating methodologies specific to their areas.
 Ionescu et.
-al \cite{fraudfinance} charectarize the types and sources cyber frauds in global digital netowrks.
-The authors link the exponential increase of cyber fraud to increased Internet usage for financial management and transactions, especially in financial markets.
-They suggest the involement of all stakeholders and employees through awareness and training for contiaining and mitigating this type of fraud.
+al \cite{ionescu2011fraud} characterize the types and sources cyber frauds in global digital networks, they link the increase of financial fraud to the prevalent usage of Internet services for financial management and transactions.
+The authors suggest the involvement of all stakeholders and employees through awareness and training for containing and mitigating fraud.
 Similarly, Howard et.
-al \cite{cybertrends} study malicious code attacks against financial networks and suggest technical detection and mitigation techniques for financial infrastructure.
-\cite{playingfield} studies how the cyber criminals have several potential advantages over the law enforcement agencies that they are opposing them.
+al \cite{howard2007cyber} study malicious code attacks against financial networks and suggest technical detection and mitigation techniques for financial infrastructure.
+\cite{piper2002} studies how the cyber criminals have several potential advantages over their opposing law enforcement agencies.
 They suggest some practical steps to even out the differential gap.
 
-Due to an increase in overall concern for online crimimal activity, there have also been state sponsered research that look af Fra have Smyth et.
-al \cite{fraudcanada} measured the extent of cyber fraud in Canada in 2011.
-Their work indicated that a major chunk of frauds do not get recorded and suggested a need of a sentinel to record fraud data similar to the FTC complaint center in the US.
+Due to an increase in the overall concern for online fraudulent activity, there has also been state-sponsored research that measures the impact of fraud.
+Smyth et.
+al \cite{smyth2011measuring} measure the extent of cyber fraud in Canada in 2011.
+Their work indicates that a major chunk of frauds does not get recorded and suggest a need for a sentinel record fraud data, similar to the FTC complaint center in the US.
 
-Another siginficnat area of research focuses on understanding the underlying demographics of vitcims of these frauds.
-A recent FTC Report \cite{ftccomplaints} use complaint data to evaluate qunatify complaint rates and nature across different ethinic and education groups.
-Reseachers in \cite{databreach} provide a comprehensive survey report collected from individials that were victims of an online data breach.
-They categorize their results in different income, education, age and ethinic groups.
-Such reseach aims at allowing organizations to better develop policies and create awarenerss among for consumer rights protections.
+Another significant area of research focuses on understanding the demographics of fraud victims.
+A recent FTC Report \cite{raval2016determines} uses complaint data to quantify complaint rates and across different ethnic and education groups in the US.
+\cite{garrett2010consumers} also look at how demographics effect the likelihood of an individual to complain about fraud.
+Researchers in \cite{ablon2016consumer} provide a comprehensive survey report that sums the reactions of the victims of an online data breach.
+They categorize their results in different income, education, age, and ethnic groups.
+Such research aims to provide organizations with informed insight to better develop policies for consumer rights protection.
 
-In comparison to previous reseach which study either cyber of regular fraud, our work provides a different angle of evaluation byat charectarizing both types of frauds and provide distinctions for each category based on popular demographics.
+In comparison to previous research which individually look at either cyber of regular fraud, w work provides a unique angle of evaluation.
+We evaluate characteristics for both types of cyber and regular frauds and their demographic trends.
 
-Our study mainly fo
+\section{Data and Calibration} \label{data-cal}
 
-\section{Data Collection}
+In this section we explain the characteristics of our datasets and the sources they were obtained from.
+We also provide insight into the essential data processing and calibration methodology that we incorporate to classify and filter the data for a fair evaluation of our questions.
 
-\section{Evaluation}
+\subsection{Data Description}
 
-\section{Discussion}
+\subsubsection{FTC Complaint Dataset}
 
-\section{Conclusion}
-The conclusion goes here.
+\begin{table}[h]
+\centering
+\begin{tabular}{c|c}
+\hline
+{\bfseries Description} & \multicolumn{1}{c}{\bfseries Value}
+\\
+\hline
+\hline
+\% Cyber Complaints &52.1\\
+\hline
+\% Regular Complaints & 47.9\\
+\hline
+Moth with Most Compliants & July 2013\\
+\hline
+Moth with Least Compliants & Feb 2013\\
+\hline
+\end{tabular}
+\vspace{8pt}
+\caption{t-test results for cyber and regular frauds in different periods}\label{ttest}
+\vspace{-10pt}
+\end{table}
 
-\section*{Acknowledgment}
+The primary dataset that we use for our evaluation is a corpus of the complaint logs filed at different collections agencies and reported to the FTC during the months Jan 2013 to June 2014.
+The Dataset is comprised of 865K complaints aggregated for cyber as well as regular fraud instances during the time period.
+Table \ref{ftcdata} shows the fields of the original dataset along with their description summary.
+For the purposes of brevity, we only include the fields that were used in our analysis.
+\\
+\subsubsection{US Census Datasets}
+Zip code information in our complaint dataset allows us to perform demographic analysis of the frauds.
+We obtain the demographic information associated with zip codes available at the US Census Bureau website \cite{uscensus}.
+The specific information that we collect is stated below:
 
-The authors would like to thank...
+\begin{itemize}
+\vspace{8pt}
+  \item Population density per zip code
+  \item Education and income data \footnote{We obtained education data was obtained from \cite{zipatlas}.}
+  \item Age statistics
+  \item Race and ethnic information
+  \vspace{8pt}
+\end{itemize}
 
-\begin{thebibliography}{1}
+As zip codes provide a low level granularity, to aggregate adjacent zip codes we obtain the Zip codes to the Metropolitan Statistical Area (MSA) mappings from \cite{uslaborstats}.
+MSA are essentially groups of geographically connected zip codes that demonstrate strong social and economic linkage.
+While there are more than 40,000 zip codes in the United States there are only 382 distinct MSAs \cite{uscensus}.
 
-\bibitem{IEEEhowto:kopka}
-H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
-  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.
+\subsection{Calibration Methodology}
 
-\bibitem{affiliate}
-pete snyder affiliate fraud
+As the FTC dataset was aggregated for all fraud channels a major calibration step we perform is to tag each crime complaint as either cyber or regular.
+An associated challenge for this was our limited view of the fraud description.
+To perform this calibration we use the \textbf{Contact Method} and \textbf{Fraud Description} fields from Table \ref{ftcdata}.
+We flag a complaint as cyber if the victims primary contact method was through online media, these are primarily websites, social networks, email and IM.
+For the remainder of the complaints we look at the description.
+If the complaint description involves something associated with Internet, we classify it as a cyber fraud regardless of how the victim was initially approached.
+Figure \ref{classify} provides an depiction of our classification methodology.
+This process  provides us with two distinct categories  and enables a fair comparison of the frauds.
 
-\bibitem{fraudfinance}
-cyberfraud in a global digital network
+\begin{figure}[t]
+\centering
+  \includegraphics[scale=0.28]{graphics/methodology.png}
+  \caption{Classification Methodology for Regular and Cyber Fraud}
+  \label{classify}
+\end{figure}
 
-\bibitem{databreach}
-Consumer Attitudes Toward Data Breach Noti cations and Loss of Personal Information
+\section{Evaluation}\label{eval}
 
-\bibitem{playingfield}
-An Uneven Playing Field: The Advantages of the Cyber Criminal vs. Law Enforcement-and Some Practical
+Our evaluation section can be divided into two main components.
+First, we look at the different aspects and trends within the complaint dataset and elaborate on certain prominent characteristics between regular and cyber frauds.
+The second part of our evaluation focuses on an in-depth analysis of the demographics linked with the fraud types.
 
-\bibitem{identitytheft}
-Identity Theft as a Teachable Moment
+\subsection{Fraud Variation over Time}
 
-\bibitem{cybertrends}
-Cyber Fraud Trends and Mitigation
+\begin{table}[b]
+\centering
+\begin{tabular}{cc}
+\hline
+\multicolumn{1}{c}{\bfseries Fraud Type} & \multicolumn{1}{c}{\bfseries \emph{p-value}
+Coefficient}
+\\
+\hline
+\hline
+Cyber & 0.014\\
+\hline
+Regular & 0.003\\
+\hline
+\end{tabular}
+\vspace{8pt}
+\caption{t-test results for cyber and regular frauds in different periods}\label{ttest}
+\vspace{-10pt}
+\end{table}
 
-\bibitem{fraudcanada}
-Cyberfraud in Canada
+We initially perform a temporal analysis of the 15-month dataset to evaluate how the fraud reporting varies, over time and explore when a certain fraud is more likely to be reported.
+As a limitation of our dataset\footnote{The dataset had significant missing values for the date if initial contact of fraud, Figure \ref{reportingfig} (a) shows that approximately 70\% of reporting dates were within a week of the date when the incident occurred.}, we use the reporting date as an estimate of fraud count for a specific date.
+While the overall rate of fraud remains consistent, we observe significant variations in the winter holiday season.
+To investigate this, we select two distinct, 20 day periods in the dataset; we label them as \textbf{Working} (Aug, 15  to Sept, 5) and \textbf{Holiday} (Dec 15, to Jan, 5).
+Figure \ref{temporal} shows the variation of cyber and regular frauds within the two specific time periods.
+We observe a significant drop in the frauds during the the holiday time period.
+Individually, cyber fraud decreases by 26\% while  regular fraud decreases by a much larger value of 56\%.
+We believe that the larger decrease in regular frauds is an overestimate as result of a bias that we explain using additional findings from the next section.
 
-\bibitem{ukphone}
-Controlling Cell Phone Fraud in the US: Lessons for the UK ‘Foresight’ Prevention Initiative
+\begin{figure}[t]
+\centering
+  \includegraphics[scale=0.35]{graphics/reg_vs_holiday.pdf}
+  \caption{Cyber and regular fraud variation during regular and holiday season}
+  \label{temporal}
+\end{figure}
 
-\bibitem{creditfraud}
-Neural data mining for credit card fraud detection
+\subsection{Fraud Reporting Methods}\label{reportingmethods}
+Consumers have the ability to report complaints to the FTC via several methods and agencies.
+We aggregate the 26 complaint collecting entities into online and offline categories.
+For instance, reports made via the Internet complaint center or the FTC complaint assistant and tagged as online, while the ones issued to the FTC call center, publisher clearing house, attorney generals or other regulatory institutions are categorized and offline.
+Figure \ref{reportingfig} provides the distribution of how individuals opt to report cyber and regular crimes.
+Approximately 82\% of cyber fraud victims used an online complaint facility, and 63\% of regular fraud victims reported via offline methods.
 
-\bibitem{phoenfraudnn}
-Detection of mobile phone fraud using supervised neural networks: A first prototype
+ \begin{figure}[b]
+\centering
+  \includegraphics[scale=0.35]{graphics/reporting_methods.pdf}
+  \caption{Distribution of reporting methods in for cyber and regular frauds}
+  \label{cdffig}
+\end{figure}
 
-\bibitem{phonefraudstat}
-Statistical Fraud Detection: A Review
+A major chunk of regular frauds are reported to offline institutions which have reduced operation during holidays.
+We believe this significantly contributes to the reduction bias of regular frauds value in Figure \ref{temporal}.
+To further validate this bias, we perform a t-test for the two fraud categories across the working and holiday time periods.
+The statistically significant \emph{p-value} for regular frauds in Table \ref{ttest}, rejects our null hypothesis of \emph{identical reporting trends between two the two time periods}.
+Additionally, we also calculate the percent increase in reporting between the last 10 holidays and 10 working days right after.
+While cyber reports only incase by 37\% the increase in regular fraud reports is a staggering 104\%.
+The ratio of increases is in line with the proportions (17:66) for offline reporting methods used by cyber and regular fraud victims.
+We believe that while both types of frauds experience a decrease, the decrease in cyber frauds represents a more accurate trend.
+These derived insights enable us to suggest more meaningful measures in section \ref{discussion} to deal with consumer fraud.
 
-\bibitem{ftcfraud}
-http://gotaclassaction.com/wp-content/uploads/2013/05/FTC-Fraud-Survey.pdf
+\subsection{Consumer Reaction Time}\label{fraudsters}
 
-\bibitem{ftccomplaints}
-complaints ftc
+We evaluate how quick do the victims of a fraud report an incident.
+Figure \ref{cdffig} (a) shows the CDF of the number of days between the date when the fraud occurred and when in was first reported to the FTC.
+We do not observe any difference between the reaction time trends of cyber and regular fraud victims.
+The graph shows that for both fraud categories, almost 30\% of the individuals take more than a week to respond.
+We believe that this provides ample time window for fraudsters to maliciously act on the assets acquired from individuals.
+This increased delay can also be a result of individuals discovering they were victimized to a fraud at a later date that the actual incident.
+One example would be of a credit card theft, when the victims only realizes after they see an unauthorized transaction.
+Unfortunately, we do have enough information in the dataset to normalize against this trend.
 
-\end{thebibliography}
+\subsection{Most Common Frauds}\label{fraudsters}
+
+Table \ref{topfrauds} provides a summary of the top frauds in each category.
+The significant cyber presence of impostor scams, and sweepstakes in, which have long existed in the regular fraud domain provides evidence that fraudsters are adopting new technology to execute the same frauds.
+We incorporate this specific insight in our discussion in section.
+Our results greatly match with the top sources of frauds in the FTC correlate with the frauds stated in an FTC news release in 2016 \cite{ftcpress2016}.
+
+\begin{table}[h]
+\centering
+\begin{tabular}{c|c||c|c}
+\hline
+\bfseries Cyber & \bfseries \% & \bfseries Regular & \bfseries \% \\
+\hline
+\hline
+Online Shopping \& Sales & 14.1 & Impostor Fraud & 29.8\\
+\hline
+Impostor Fraud & 10.8 & Telemarketing & 20.1\\
+\hline
+Unsolicited Email & 7.71 & Debt Collection & 16.1\\
+\hline
+Counterfeit Check Scams	 & 7.40 & Prizes \& Sweepstakes & 15.5 \\
+\hline
+Prizes \& Sweepstakes & 7.40 & Grants \& Credit Loans & 4.14\\
+\hline
+\hline
+\end{tabular}
+\vspace{8pt}
+\caption{Top Fraud Types}\label{topfrauds}
+\vspace{-15pt}
+\end{table}
+
+\subsection{Top Fraudster Locations}\label{fraudsters}
+Next, we identify the primary locations of the fraudsters within the United States and present our findings in ref{topareas}.
+While fraudulent entities are spread throughout, most of the heavy hitters belong to the metropolitan areas.
+We believe this provides an efficient disguise to the fraudulent entities.
+Numbers: 29.3\% cyber reports and 32.6\% regular reports.
+
+\begin{table}[h]
+\centering
+\begin{tabular}{c|c|c}
+\hline
+\bfseries Metropolitan Area (MSA) & \bfseries \% Cyber & \bfseries \% Regular\\
+\hline
+\hline
+New York, New Jersey, Long Island & 8.41 & 7.67 \\
+\hline
+Los Angeles, Long Beach, Santa Ana & 6.50 & 7.09 \\
+\hline
+Washington, Arlington, Alexandria & 4.10 & 5.78 \\
+\hline
+Miami-Fort Lauderdale, Pompano Beach & 4.16 & 5.40 \\
+\hline
+Dallas, Fort Worth, Arlington & 2.89 & 3.36\\
+\hline
+Chicago, Naperville Joliet & 3.17 & 3.27 \\
+\hline
+\end{tabular}
+\vspace{8pt}
+\caption{Top Metropolitan Areas Where Fraudsters are Based}\label{topareas}
+\vspace{-15pt}
+\end{table}
+
+We also observe certain areas that have a high cyber to regular fraud ratio and vice versa.
+The San Franciso, Oakland and San Jose, Santa Clara MSAs have a cyber to regular fraud ratio of 2.21 and 5.13.
+The popular fraud types in these regions are Internet services, unsolicited email, and online shopping.
+These areas serve as a good medium for cyber fraudsters as it allows them to gel into the surrounding cyber industry.
+Meanwhile, The Buffalo, Niagara Falls MSA has a regular to cyber fraud ratio of 8.76 with debt collection being the significant outlier.
+Further investigation reveals that Buffalo has a network of debt collecteors which have responsible for multi-million frauds \cite{buffalodebt1, buffalodebt2}.
+
+\subsection{Fraudster Coverage}\label{fraudstercoverage}
+
+In order to understand the operational regions of fraudulent entities, we calculate the distances between consumer and fraudster zip codes.
+Figure \ref{reportingfig} (b) provides a cumulative distribution of the operational radii for cyber and regular fraudsters.
+This analysis provides insight on weather cyber fraudsters leverage the Internet for more visibility and access to target more distant individuals.
+With a median distance of 993 and 861 for cyber and regular frauds, we believe that both types of fraudsters follow similar trends.
+This indicates that a major the Internet based communication does not provide cyber fraudsters with significant advantage over regular ones as they are able to achieve similar operational spans by using phone and mail based communication methods.
+
+\begin{figure}[t]
+\centering
+  \includegraphics[scale=0.28]{graphics/dist_days.pdf}
+  \caption{Distribution of reporting methods in for cyber and regular frauds}
+  \label{reportingfig}
+\end{figure}
+
+\subsection{Demographic Analysis}\label{fraudsters}
+
+\begin{table*}[h]
+\noindent
+\centering
+\begin{tabular}{c||c|c|c||c|c|c}
+\hline
+\multicolumn{1}{c||}{\bfseries } & \multicolumn{3}{c||}{\bfseries Cyber Complaints} & \multicolumn{3}{c}{\bfseries Regular Complaints}\\
+\hline
+\bfseries Observed Variable & \bfseries Coefficient & \bfseries \emph{p-value} & \bfseries 95\% Confidence Interval & \bfseries Coefficient & \bfseries \emph{p-value} & \bfseries 95\% Confidence Interval \\
+\hline
+White (Non-Hispanic) & -0.0042 & 0.074 & [-0.009, 0] & -0.0013 &  0.128 & [0.003,  0]\\
+\hline
+Black & -0.0058 & 0.017 & [-0.011, -0.001] & 0.0017 & 0.054 & [-2.77$^{-5}$, -0.003]\\
+\hline
+Asian & -0.0025 & 0.468 & [-0.009, 0.004] & -0.0051 & 0.00 & [-0.008, -0.003]\\
+\hline
+Hispanic & -0.0026 & 0.014 & [-0.05, -0.001] & -0.0054 & 0.00 & [-0.006, -0.005]\\
+\hline
+Age & 0.0064 & 0.023 & [ 0.001, 0.012] & 0.0281 & 0.00 & [0.026, 0.030]\\
+\hline
+Income & -2.226$^{-6}$ & 8.85$^{-7}$ & [-3.96$^{-6}$ , -4.92$^{-7}$] & -3.695$^{-6}$ & 0.000  & [-4.31$^{-6}$, -3.08$^{-6}$]\\
+\hline
+Education & 0.0155 & 0.000 & [0.013, 0.018] & 0.0044 & 0.00 & [0.003, -0.005]\\
+\hline
+Unemployment & 0.0084 & 0.111 & [-0.002, 0.019] & -0.0028 & 0.138 & [-0.006, 0.001]\\
+\hline
+\end{tabular}
+
+\vspace{8pt}
+\caption{The description of the data fields that were primarily used in the for data calibration and analysis}\label{regressions}
+\vspace{-20pt}
+\end{table*}
+
+\begin{figure}[b]
+\centering
+  \includegraphics[scale=0.29]{graphics/demographics.pdf}
+  \caption{Cyber and regular fraud trends over age, income, education and unemployment.}
+  \label{demographics}
+\end{figure}
+To evaluate the effect of prominent demographic features we perform a logistic regression for both cyber and regular complaint rates.
+Table \label{regressions} summarizes our coefficients and their significance.
+Among ethnicities, our results generate statistically significant results for only Hispanic communities.
+While the coefficients suggest that frauds decrease for heavier concentrations of  Hispanics, a survey study \cite{anderson2013consumer} showed that Hispanics and Black communities are more likely to be victims of crimes.
+The decreasing trend is actually a result of fraud underreporting due to cultural reasons, distrust in agencies the lack of awareness and education \cite{consumerlessons}.
+
+Other socio economic variables that we take into account are age, income, education an the rate of unemployment.
+In addition to the regression analysis, we investigate their variation by observing complaint rates across their distributions in Figure \ref{demographics}.
+
+\textbf{Age:} While the differences in cyber and regular complaints remain fairly consistent, from Figure \cite{demographics} (a) we observe that individuals greater that 50 years complain significantly more than other age groups.
+Our significant regression values also corroborate to this trend.
+
+\textbf{Education:} Both cyber and regular complaints increase along with an increase in percentage education.
+We associate this trend with greater increased educational awareness among individuals \cite{consumerlessons}.
+Another subtle trend, in the increase in cyber to regular complaint ratio from 0.82 to 1.23.
+We associate this diverging trend to more educated individuals being active  the Internet  more frequently, and hence being more prone to online fraud{pewcollege}.
+Our reasoning is in line with insights from our regression analysis which additionally normalizes for other factors.
+
+We do include income and unemployment in our analysis due to their insignificant correlation values in Table \ref{regressions}.
+
+\section{Discussion}\label{discussion}
+Based on our findings from section \ref{eval}, we elaborate some discussion points in hopes that they will assist in the development of better policies and will help prevent consumer fraud in the U.S.
+
+Our results indicate that while cyber frauds are on the rise, regular fraud methods still hold an equally significant share in the economy, and while policy developments are trending towards mitigating online fraud, there should be continuous awareness campaigns for phone, mail and other regular fraud types.
+As a result of reduced operational hours in the winter holidays, offline collection agencies experience an uneven decrease followed by a great influx of reports on resuming operation.
+To streamline the process, online reporting methods should be promoted.
+
+We also learn that fraudulent entities tend to work in groups and establish networks \cite{buffalodebt2}.
+The fraudulent cyber establishments of San Jose and San Francisco discussed in section \ref{fraudsters}, help us understand that fraudulent entities use strategic measures to gel-in with the legitimate industry.
+This necessitates the need for stricter policies while registering organizations with the State agencies.
+Localization of fraudsters also allows inspection teams to target efficiently.
+By observing overlap between top cyber and regular frauds (Table \ref{topfrauds}) we realize that with the rise of Internet, fraudsters have their methodologies to execute scams on the Internet that were initially perpetrated through regular methods.
+We suggest that policy makers should work closely with technologists to devise advanced learning mechanisms similar to \cite{brause1999neural, moreau1997detection} which enables the filtering and control of fraud.
+
+\section{Conclusion and Future Work}\label{conclusion}
+
+The goal of this paper is to provide a comprehensive comparison of cyber and regular consumer fraud in the United States.
+By applying an efficient classification and measurement methodology on an FTC complaint dataset, we explore trends among cyber and regular fraud, in time, distance and location metrics as well as their variation across consumer demographics.
+Based on our findings, we suggest insights to aid policy development for fraud prevention.
+In future, we look forward to working closely with regulatory organizations and provide data driven policy insights.
+
+\bibliographystyle{IEEEtran}
+
+\bibliography{references}
 

### 2017-01-18 paper/paper.tex
added .gitignore for latex, and spelling
abstract

@@
 This paper investigates the differences in fraud reporting and targeting among United States based consumers by comparing fraudulent activity mediated by the Internet, with traditional forms of fraud.
-We find that \ck{ADD QUICK AND EASY CONCLUSIONS HERE}.
+Both categories of frauds experience a decrease during the holiday season.
+We study Interestingly, individuals who are victimized via traditional methods are more likely to complain using phone or in-person, while 82\% of the cyber victims use an online resource to  generate fraud complaints.
+
+ \ck{ADD QUICK AND EASY CONCLUSIONS HERE}.
 
@@
 
-In the United States, a total of more that 25 million people are victims of frauds \ck{per year?} \cite{anderson2013consumer}.
+In the United States, a total of more that 25 million people are victims of frauds per year.
+\cite{anderson2013consumer}.
 These deceptive scams are a major cause of economic damages to users, not to mention the added externalities of wasted time and stress.
@@
 \vspace{8pt}
-\caption{The description of the data fields that were primarily used in the for data calibration and analysis}\label{ftcdata}
+\caption{data field descriptions primarily used for data calibration and analysis}\label{ftcdata}
 \vspace{-20pt}
@@
 \hline
-Moth with Most Compliants & July 2013\\
+Month with Most Complaints & July 2013\\
 \hline
-Moth with Least Compliants & Feb 2013\\
+Month with Least Complaints & Feb 2013\\
 \hline

### 2017-01-18 paper/paper.tex
table tweak

--- 2017-01-18 paper/paper.tex
@@
 If the complaint description involves something associated with Internet, we classify it as a cyber fraud regardless of how the victim was initially approached.
-Figure \ref{classify} provides an depiction of our classification methodology.
+Figure \ref{classify} provides a depiction of our classification methodology.
 This process  provides us with two distinct categories  and enables a fair comparison of the frauds.
@@
 \hline
-\multicolumn{1}{c||}{\bfseries } & \multicolumn{3}{c||}{\bfseries Cyber Complaints} & \multicolumn{3}{c}{\bfseries Regular Complaints}\\
+\multicolumn{1}{c||}{\bfseries } & \multicolumn{3}{c||}{\bfseries Cyber Complaints Per Capita} & \multicolumn{3}{c}{\bfseries Regular Complaints Per Capita}\\
 \hline
@@
 \hline
-White (Non-Hispanic) & -0.0042 & 0.074 & [-0.009, 0] & -0.0013 &  0.128 & [0.003,  0]\\
+\% White (Non-Hispanic) & -0.0042 & 0.074 & [-0.009, 0] & -0.0013 &  0.128 & [0.003,  0]\\
 \hline
-Black & -0.0058 & 0.017 & [-0.011, -0.001] & 0.0017 & 0.054 & [-2.77$^{-5}$, -0.003]\\
+\% Black & -0.0058 & 0.017 & [-0.011, -0.001] & 0.0017 & 0.054 & [-2.77$^{-5}$, -0.003]\\
 \hline
-Asian & -0.0025 & 0.468 & [-0.009, 0.004] & -0.0051 & 0.00 & [-0.008, -0.003]\\
+\% Asian & -0.0025 & 0.468 & [-0.009, 0.004] & -0.0051 & 0.00 & [-0.008, -0.003]\\
 \hline
-Hispanic & -0.0026 & 0.014 & [-0.05, -0.001] & -0.0054 & 0.00 & [-0.006, -0.005]\\
+\% Hispanic & -0.0026 & 0.014 & [-0.05, -0.001] & -0.0054 & 0.00 & [-0.006, -0.005]\\
 \hline

### 2017-01-18 paper/paper.tex
reworked concl

@@
 While the coefficients suggest that frauds decrease for heavier concentrations of  Hispanics, a survey study \cite{anderson2013consumer} showed that Hispanics and Black communities are more likely to be victims of crimes.
-The decreasing trend is actually a result of fraud underreporting due to cultural reasons, distrust in agencies the lack of awareness and education \cite{consumerlessons}.
+The decreasing trend is likely a result of fraud under-reporting due to cultural reasons, distrust in institutions, and lack of awareness or education \cite{consumerlessons}.
 
-Other socio economic variables that we take into account are age, income, education an the rate of unemployment.
+Other socio-economic variables that we take into account are age, income, education an the rate of unemployment.
 In addition to the regression analysis, we investigate their variation by observing complaint rates across their distributions in Figure \ref{demographics}.
@@
 Another subtle trend, in the increase in cyber to regular complaint ratio from 0.82 to 1.23.
-We associate this diverging trend to more educated individuals being active  the Internet  more frequently, and hence being more prone to online fraud{pewcollege}.
+We associate this diverging trend to more educated individuals being active  the Internet  more frequently, and hence being more prone to online fraud~\cite{pewcollege}.
 Our reasoning is in line with insights from our regression analysis which additionally normalizes for other factors.
@@
 \section{Discussion}\label{discussion}
-Based on our findings from section \ref{eval}, we elaborate some discussion points in hopes that they will assist in the development of better policies and will help prevent consumer fraud in the U.S.
+Based on our findings from section \ref{eval}, we elaborate some discussion points to provide context for this analysis in hopes that it will assist in the development of better policies and help reduce consumer fraud in the U.S.
 
@@
 We also learn that fraudulent entities tend to work in groups and establish networks \cite{buffalodebt2}.
-The fraudulent cyber establishments of San Jose and San Francisco discussed in section \ref{fraudsters}, help us understand that fraudulent entities use strategic measures to gel-in with the legitimate industry.
-This necessitates the need for stricter policies while registering organizations with the State agencies.
-Localization of fraudsters also allows inspection teams to target efficiently.
-By observing overlap between top cyber and regular frauds (Table \ref{topfrauds}) we realize that with the rise of Internet, fraudsters have their methodologies to execute scams on the Internet that were initially perpetrated through regular methods.
-We suggest that policy makers should work closely with technologists to devise advanced learning mechanisms similar to \cite{brause1999neural, moreau1997detection} which enables the filtering and control of fraud.
+The fraudulent cyber establishments of San Jose and San Francisco discussed in Section \ref{fraudsters}, help us understand that fraudulent entities likely reflect the makeup of nearby  legitimate industries.
+By observing the overlap between top cyber and regular frauds (Table \ref{topfrauds}) we realize that with the rise of Internet, fraudsters have their choice of vectors to execute scams  that were traditionally only perpetrated through traditional means.
+Better understanding these advanced communication  modalities requires a technologists' touch;  policy makers should consider working closely with technologists to devise detection mechanisms similar to \cite{brause1999neural, moreau1997detection} which enable better filtering and control of fraudulent activity.
 
-\section{Conclusion and Future Work}\label{conclusion}
+\section{Conclusion}\label{conclusion}
 
-The goal of this paper is to provide a comprehensive comparison of cyber and regular consumer fraud in the United States.
-By applying an efficient classification and measurement methodology on an FTC complaint dataset, we explore trends among cyber and regular fraud, in time, distance and location metrics as well as their variation across consumer demographics.
-Based on our findings, we suggest insights to aid policy development for fraud prevention.
-In future, we look forward to working closely with regulatory organizations and provide data driven policy insights.
+The goal of this paper is to investigate the dynamics of cyber and traditional methods for committing  fraud in the United States.
+By partitioning the FTC Consumer Sentinel complaint dataset, we are able to explore trends among cyber and regular fraud, and analyze trends along time, distance and location metrics as well as their variation across consumer demographics.
+While the Internet has greatly expanded the potential reach and scale of fraudsters: where once they could only use mail or telephones for various frauds, the Internet enables one to contact millions of users very quickly, whether through fraudulent websites, Craigslist posts, or spam emails.
+Even so, the difference between the cyber and non-cyber methodologies is not overwhelming: this effect suggests that non-cyber activities, like purchasing goods or posting money orders, may still serve as a limiting factor on the extent or targeting of these fraudulent activities.
 

### 2017-01-18 paper/paper.tex
minor edits

--- 2017-01-18 paper/paper.tex
@@
 This paper investigates the differences in fraud reporting and targeting among United States based consumers by comparing fraudulent activity mediated by the Internet, with traditional forms of fraud.
-Both categories of frauds experience a decrease during the holiday season.
-We study Interestingly, individuals who are victimized via traditional methods are more likely to complain using phone or in-person, while 82\% of the cyber victims use an online resource to  generate fraud complaints.
+We study the difference in fraud trends across time, location, ethnic and socio-economic factors.
+Both categories of frauds experience an overall decrease during the holiday season.
+Individuals who are victimized via traditional methods are more likely to complain using phone or in-person, while a majority of cyber victims submit fraud complaints online.
+By evaluating the top frauds in each category, we demonstrate how traditional fraudsters have evolved in their operational methodologies to execute scams on the Internet that were initially perpetrated through traditional means.
 
@@
 
-\textbf{Age:} While the differences in cyber and regular complaints remain fairly consistent, from Figure \cite{demographics} (a) we observe that individuals greater that 50 years complain significantly more than other age groups.
+\textbf{Age:} While the differences in cyber and regular complaints remain fairly consistent, from Figure \ref{demographics} (a) we observe that individuals greater that 50 years complain significantly more than other age groups.
 Our significant regression values also corroborate to this trend.

### 2017-01-18 paper/paper.tex

--- 2017-01-18 paper/paper.tex
@@
 This paper investigates the differences in fraud reporting and targeting among United States based consumers by comparing fraudulent activity mediated by the Internet, with traditional forms of fraud.
-We find that \ck{ADD QUICK AND EASY CONCLUSIONS HERE}.
+We study the difference in fraud trends across time, location, ethnic and socio-economic factors.
+Both categories of frauds experience an overall decrease during the holiday season.
+Individuals who are victimized via traditional methods are more likely to complain using phone or in-person, while a majority of cyber victims submit fraud complaints online.
+By evaluating the top frauds in each category, we demonstrate how traditional fraudsters have evolved in their operational methodologies to execute scams on the Internet that were initially perpetrated through traditional means.
+
+ \ck{ADD QUICK AND EASY CONCLUSIONS HERE}.
 

### 2017-01-18 paper/paper.tex
abstract

@@
 This paper investigates the differences in fraud reporting and targeting among United States based consumers by comparing fraudulent activity mediated by the Internet, with traditional forms of fraud.
-We study the difference in fraud trends across time, location, ethnic and socio-economic factors.
+We summarize the difference in fraud trends across time, distance and location metrics as well as ethnic and socio-economic factors.
 Both categories of frauds experience an overall decrease during the holiday season.
-Individuals who are victimized via traditional methods are more likely to complain using phone or in-person, while a majority of cyber victims submit fraud complaints online.
-By evaluating the top frauds in each category, we demonstrate how traditional fraudsters have evolved in their operational methodologies to execute scams on the Internet that were initially perpetrated through traditional means.
-
- \ck{ADD QUICK AND EASY CONCLUSIONS HERE}.
+Individuals who are victimized via traditional methods are more likely to complain using traditional methods, while a majority of cyber victims submit fraud complaints online.
+By evaluating the top frauds in each category, we demonstrate how traditional fraudsters have evolved in their methodologies execute scams on the Internet that were initially perpetrated through traditional means.
+Finally, based on our findings, we suggest policy based insights to strategically prevent these fraudulent activities
 
@@
   \item Population density per zip code
-  \item Education and income data \footnote{We obtained education data was obtained from \cite{zipatlas}.}
+  \item Education and income data \footnote{We obtained education data from \cite{zipatlas}.}
   \item Age statistics
@@
 
-\section{Evaluation}\label{eval}
+\section{Hypotheses and Evaluation}\label{eval}
 

### 2017-01-18 paper/paper.tex
abstract

@@
 % author names and affiliations
-%\author{\IEEEauthorblockN{Mohammad Taha Khan and Chris Kanich}
-%\IEEEauthorblockA{Department of Computer Science, University of Illinois at Chicago\\taha@cs.uic.edu, ckanich@uic.edu}}
+\author{\IEEEauthorblockN{Mohammad Taha Khan and Chris Kanich}
+\IEEEauthorblockA{Department of Computer Science, University of Illinois at Chicago\\taha@cs.uic.edu, ckanich@uic.edu}}
 
@@
 This paper investigates the differences in fraud reporting and targeting among United States based consumers by comparing fraudulent activity mediated by the Internet, with traditional forms of fraud.
-We summarize the difference in fraud trends across time, distance and location metrics as well as ethnic and socio-economic factors.
-Both categories of frauds experience an overall decrease during the holiday season.
+By partitioning the FTC Consumer Sentinel complaint dataset into cyber and traditional categories, we summarize the difference in fraud trends across time, distance and location metrics.We also evaluate fraud variations across different ethnic and socio-economic factors.
+
+Our findings suggest that both categories of frauds experience an overall decrease during the holiday season.
 Individuals who are victimized via traditional methods are more likely to complain using traditional methods, while a majority of cyber victims submit fraud complaints online.
-By evaluating the top frauds in each category, we demonstrate how traditional fraudsters have evolved in their methodologies execute scams on the Internet that were initially perpetrated through traditional means.
-Finally, based on our findings, we suggest policy based insights to strategically prevent these fraudulent activities
+By evaluating the top frauds in each category, we demonstrate how traditional fraudsters have evolved in their methodologies to execute scams on the Internet that were initially perpetrated through traditional means.
+Finally, we incorporate our results to suggest policy based insights to strategically prevent these fraudulent activities
 
@@
 We also collect demographic information from the US Census Bureau \cite{uscensus}.
-In addition to data collection, we devise a calibration methodology to identify and separate cyber frauds from non-cyber in the complaint dataset.
+In addition to data collection, we devise a calibration methodology to identify and separate cyber frauds from non-cyber (regular) in the complaint dataset.
 
@@
 First, we evaluate the distinctive trends prevalent in cyber and regular frauds in the dataset.
-This encompasses their reporting numbers and methods.
-The nature of frauds which are more common in each specific category and the insights on the fraudsters who carry out these specific deceptive activities.
-Secondly, we look at ethnic, age, education and employment demographics in each specific category and evaluate if certain individuals are more likely to report crimes.
-Finally, based on our findings we provide suggestive measures that can be taken into account by regulatory agencies to reduce the overall fraud in the United States.
+This encompasses their reporting numbers and methods, the nature of frauds which are more common in each specific category as well as the insights on the fraudsters who carry out these specific deceptive activities.
+Secondly, we look at ethnic, age, education, and employment demographics in each specific category and evaluate if certain individuals are more likely to report crimes.
+Finally, based on our findings we suggest measures that can be taken into account by regulatory agencies to reduce the overall fraud in the United States.
 
@@
 In section \ref{data-cal}, we elaborate features of the datasets used in our analysis along with a description of our calibration methodology.
-Section \ref{eval} summarizes our findings from the data followed by our suggestions to regulatory agencies in \ref{discussion}.
+Section \ref{eval} summarizes our findings from the data, followed by our suggestions to regulatory agencies in \ref{discussion}.
 We conclude our work in section \ref{conclusion} and discuss avenues of future research.
@@
 \vspace{8pt}
-\caption{data field descriptions primarily used for data calibration and analysis}\label{ftcdata}
+\caption{data field primarily used for data calibration and analysis}\label{ftcdata}
 \vspace{-20pt}
@@
 As our work evaluates both cyber as well as regular frauds, we provide related work that encompasses both of these categories.
-However, we elaborate more on recent research which focuses on cyber frauds as more individuals are victims of these crimes \cite{anderson2013consumer} due to the increased Internet usage trends for sensitive activities.
-Before the Internet became a primary hub of economic and social activity, researchers measured \cite{clarke2001controlling} and developed techniques based on statistical models \cite{brause1999neural, moreau1997detection, bolton2002statistical, snyder2015no} to detect phone and credit card based frauds.
-In the past few years,  research evaluations have shifted focus towards cyber activity \cite{ablon2016consumer, piper2002, ionescu2011fraud, howard2007cyber} due to its high rate and the increased potential for harm.
+Before the Internet became a primary hub of economic and social activity, researchers measured \cite{clarke2001controlling} and developed techniques based on statistical models \cite{brause1999neural, moreau1997detection, bolton2002statistical} to detect phone and credit card based frauds.
+In the past few years,  research evaluations have shifted focus towards cyber activity \cite{ablon2016consumer, piper2002, ionescu2011fraud, howard2007cyber, snyder2015no} due to the increased Internet usage trends for sensitive activities and its increased potential for harm.
 
@@
 Ionescu et.
-al \cite{ionescu2011fraud} characterize the types and sources cyber frauds in global digital networks, they link the increase of financial fraud to the prevalent usage of Internet services for financial management and transactions.
+al \cite{ionescu2011fraud} characterize the types and sources cyber financial frauds in global digital networks.
 The authors suggest the involvement of all stakeholders and employees through awareness and training for containing and mitigating fraud.
@@
 Another significant area of research focuses on understanding the demographics of fraud victims.
+\cite{JOCA:JOCA1}.
 A recent FTC Report \cite{raval2016determines} uses complaint data to quantify complaint rates and across different ethnic and education groups in the US.
@@
 
-In comparison to previous research which individually look at either cyber of regular fraud, w work provides a unique angle of evaluation.
+In comparison to previous research which individually look at either cyber or regular fraud, our work provides a unique angle of evaluation.
 We evaluate characteristics for both types of cyber and regular frauds and their demographic trends.
@@
 \vspace{8pt}
-\caption{t-test results for cyber and regular frauds in different periods}\label{ttest}
+\caption{Summary Statistics of the FTC dataset}\label{ttest}
 \vspace{-10pt}
@@
 
-The primary dataset that we use for our evaluation is a corpus of the complaint logs filed at different collections agencies and reported to the FTC during the months Jan 2013 to June 2014.
-The Dataset is comprised of 865K complaints aggregated for cyber as well as regular fraud instances during the time period.
+The primary dataset that we use for our evaluation is a corpus of the complaint logs filed at different collections agencies and reported to the FTC during the months Jan 2013 to June 2014.\footnote{This data was obtained from the directly from the FTC under the Freedom of Information Act.} The Dataset is comprised of 865K complaints aggregated for cyber as well as regular fraud instances during the time period.
 Table \ref{ftcdata} shows the fields of the original dataset along with their description summary.
@@
 To perform this calibration we use the \textbf{Contact Method} and \textbf{Fraud Description} fields from Table \ref{ftcdata}.
-We flag a complaint as cyber if the victims primary contact method was through online media, these are primarily websites, social networks, email and IM.
+We flag a complaint as cyber if the victims primary contact method was through online media; these are primarily websites, social networks, email and IM.
 For the remainder of the complaints we look at the description.
@@
   \includegraphics[scale=0.28]{graphics/methodology.png}
-  \caption{Classification Methodology for Regular and Cyber Fraud}
+  \caption{Methodology for classifying cyber and regular frauds.}
   \label{classify}
@@
 
-\section{Hypotheses and Evaluation}\label{eval}
+\section{Evaluation}\label{eval}
 
@@
 \vspace{8pt}
-\caption{t-test results for cyber and regular frauds in different periods}\label{ttest}
+\caption{t-test results for frauds across different time periods}\label{ttest}
 \vspace{-10pt}
@@
   \includegraphics[scale=0.35]{graphics/reg_vs_holiday.pdf}
-  \caption{Cyber and regular fraud variation during regular and holiday season}
+  \caption{Fraud variation during regular and holiday season}
   \label{temporal}
@@
 We aggregate the 26 complaint collecting entities into online and offline categories.
-For instance, reports made via the Internet complaint center or the FTC complaint assistant and tagged as online, while the ones issued to the FTC call center, publisher clearing house, attorney generals or other regulatory institutions are categorized and offline.
+For instance, reports made via the Internet complaint center or the FTC complaint assistant are tagged as online, while the ones issued to the FTC call center, publisher clearing house, attorney generals, or other regulatory institutions are categorized as offline.
 Figure \ref{reportingfig} provides the distribution of how individuals opt to report cyber and regular crimes.
@@
   \includegraphics[scale=0.35]{graphics/reporting_methods.pdf}
-  \caption{Distribution of reporting methods in for cyber and regular frauds}
+  \caption{Distribution of reporting methods for frauds}
   \label{cdffig}
@@
 To further validate this bias, we perform a t-test for the two fraud categories across the working and holiday time periods.
-The statistically significant \emph{p-value} for regular frauds in Table \ref{ttest}, rejects our null hypothesis of \emph{identical reporting trends between two the two time periods}.
+The statistically significant \emph{p-value} for regular frauds in Table \ref{ttest} rejects our null hypothesis of \emph{identical reporting trends across the two time periods}.
 Additionally, we also calculate the percent increase in reporting between the last 10 holidays and 10 working days right after.
-While cyber reports only incase by 37\% the increase in regular fraud reports is a staggering 104\%.
+While cyber reports only increase by 37\% the increase in regular fraud reports is a staggering 104\%.
 The ratio of increases is in line with the proportions (17:66) for offline reporting methods used by cyber and regular fraud victims.
@@
 
-We evaluate how quick do the victims of a fraud report an incident.
+We evaluate how quickly do the victims of a fraud report an incident.
 Figure \ref{cdffig} (a) shows the CDF of the number of days between the date when the fraud occurred and when in was first reported to the FTC.
@@
 We believe that this provides ample time window for fraudsters to maliciously act on the assets acquired from individuals.
-This increased delay can also be a result of individuals discovering they were victimized to a fraud at a later date that the actual incident.
-One example would be of a credit card theft, when the victims only realizes after they see an unauthorized transaction.
+This increased delay can also be a result of individuals discovering they were victimized to a fraud at a later date than the actual incident.
+One example would be of a credit card theft, when the victims only recognize the breach after they see an unauthorized transaction.
 Unfortunately, we do have enough information in the dataset to normalize against this trend.
@@
 \vspace{8pt}
-\caption{The description of the data fields that were primarily used in the for data calibration and analysis}\label{regressions}
+\caption{Regression Results for Per capita frauds evaluated for Ethnic and Socio-Economic factors}\label{regressions}
 \vspace{-20pt}

### 2017-01-18 paper/paper.tex
as submitted

@@
 
-While cybercrime is a relatively recent human invention, fraudulent activity has a much longer history.
-This paper investigates the differences in fraud reporting and targeting among United States based consumers by comparing fraudulent activity mediated by the Internet, with traditional forms of fraud.
-By partitioning the FTC Consumer Sentinel complaint dataset into cyber and traditional categories, we summarize the difference in fraud trends across time, distance and location metrics.We also evaluate fraud variations across different ethnic and socio-economic factors.
-
-Our findings suggest that both categories of frauds experience an overall decrease during the holiday season.
-Individuals who are victimized via traditional methods are more likely to complain using traditional methods, while a majority of cyber victims submit fraud complaints online.
-By evaluating the top frauds in each category, we demonstrate how traditional fraudsters have evolved in their methodologies to execute scams on the Internet that were initially perpetrated through traditional means.
-Finally, we incorporate our results to suggest policy based insights to strategically prevent these fraudulent activities
+While cybercrime is a relatively recent human invention, fraudulent activity
+has a much longer history.
+Understanding the extent to which cybercrime is fundamentally different from, or similar to, traditional fraudulent activity is the first step toward being able to effectively combat it.
+This paper investigates the differences in fraud
+reporting and targeting among United States based consumers by comparing
+fraudulent activity mediated by the Internet with traditional forms of
+fraud. By partitioning the FTC Consumer Sentinel complaint dataset into
+cyber and traditional categories, we summarize the difference in fraud
+trends across time, distance and location metrics.We also evaluate fraud
+variations across different ethnic and socio-economic factors. Our findings
+suggest that both categories of frauds experience an overall decrease during
+the holiday season. Individuals who are victimized via traditional methods
+are more likely to complain using traditional methods, while a majority of
+cyber victims submit fraud complaints online. By evaluating the top frauds
+in each category, we demonstrate how traditional fraudsters have evolved in
+their methodologies to execute scams on the Internet that were initially
+perpetrated through traditional means.
 
@@
 
-Our evaluation section can be divided into two main components.
+Our evaluation section can be divided into three main components.
 First, we look at the different aspects and trends within the complaint dataset and elaborate on certain prominent characteristics between regular and cyber frauds.
-The second part of our evaluation focuses on an in-depth analysis of the demographics linked with the fraud types.
+Next we study consumer and fraudster behaviors.
+The third part of our evaluation focuses on an in-depth analysis of the demographics linked with the fraud types.
 
@@
 Table \ref{topfrauds} provides a summary of the top frauds in each category.
-The significant cyber presence of impostor scams, and sweepstakes in, which have long existed in the regular fraud domain provides evidence that fraudsters are adopting new technology to execute the same frauds.
+The significant cyber presence of impostor scams and sweepstakes in, which have long existed in the regular fraud domain, provides evidence that fraudsters are adopting new technology to execute the same frauds.
 We incorporate this specific insight in our discussion in section.
-Our results greatly match with the top sources of frauds in the FTC correlate with the frauds stated in an FTC news release in 2016 \cite{ftcpress2016}.
+Our results greatly align with the top sources of frauds stated in an FTC news release in 2016 \cite{ftcpress2016}.
 
@@
 \vspace{8pt}
-\caption{Top Fraud Types}\label{topfrauds}
+\caption{Top Fraud Descriptions}\label{topfrauds}
 \vspace{-15pt}
@@
 \subsection{Top Fraudster Locations}\label{fraudsters}
-Next, we identify the primary locations of the fraudsters within the United States and present our findings in ref{topareas}.
+Next, we identify the primary locations of the fraudsters within the United States and present our findings in \ref{topareas}.
 While fraudulent entities are spread throughout, most of the heavy hitters belong to the metropolitan areas.
 We believe this provides an efficient disguise to the fraudulent entities.
-Numbers: 29.3\% cyber reports and 32.6\% regular reports.
 
@@
 \vspace{8pt}
-\caption{Top Metropolitan Areas Where Fraudsters are Based}\label{topareas}
+\caption{Top Fraudsters Locations}\label{topareas}
 \vspace{-15pt}
@@
 Meanwhile, The Buffalo, Niagara Falls MSA has a regular to cyber fraud ratio of 8.76 with debt collection being the significant outlier.
-Further investigation reveals that Buffalo has a network of debt collecteors which have responsible for multi-million frauds \cite{buffalodebt1, buffalodebt2}.
+Further investigation reveals that Buffalo has a network of debt collecteors which have been responsible for multi-million frauds \cite{buffalodebt1, buffalodebt2}.
 
@@
 Figure \ref{reportingfig} (b) provides a cumulative distribution of the operational radii for cyber and regular fraudsters.
-This analysis provides insight on weather cyber fraudsters leverage the Internet for more visibility and access to target more distant individuals.
+This analysis provides insight on whether cyber fraudsters leverage the Internet for more visibility and access to target more distant individuals.
 With a median distance of 993 and 861 for cyber and regular frauds, we believe that both types of fraudsters follow similar trends.
@@
   \includegraphics[scale=0.28]{graphics/dist_days.pdf}
-  \caption{Distribution of reporting methods in for cyber and regular frauds}
+  \caption{The cumulative distribution for (a) The difference between fraud and reporting dates. (b) The distance between consumers and fraudsters.}
   \label{reportingfig}
@@
 To evaluate the effect of prominent demographic features we perform a logistic regression for both cyber and regular complaint rates.
-Table \label{regressions} summarizes our coefficients and their significance.
+Table \ref{regressions} summarizes our coefficients and their significance.
 Among ethnicities, our results generate statistically significant results for only Hispanic communities.
@@
 
-We do include income and unemployment in our analysis due to their insignificant correlation values in Table \ref{regressions}.
+We do not include income and unemployment in our analysis due to their insignificant correlation values in Table \ref{regressions}.
 

### 2017-03-07 paper/paper.tex
copyedits upto section III

@@
 
-In the United States, a total of more that 25 million people are victims of frauds per year.
-\cite{anderson2013consumer}.
+In the United States, a total of more than 25 million people are victims of frauds per year \cite{anderson2013consumer}.
 These deceptive scams are a major cause of economic damages to users, not to mention the added externalities of wasted time and stress.
-These illicit practices have been a part of the underground economy for a while.
-Initially individuals were tricked by scam calls, mail or in-person fraudsters, however, the rise of the Internet has provided fraudulent entities with a more streamlined exposure to the overall population.
-A  survey report from 2014 indicated that 47\% of Americans had been victims of an online identity theft.
-Another recent report released by the  Federal Trade Commission (FTC) revealed that debt collection, identity theft, and impostor scams contribute towards 56\% of the total frauds complaints in 2015 \cite{ftcpress2016} .
+Such illicit practices have been a part of the underground economy for quite a while.
+Initially, individuals were tricked by scam calls, in-person fraudsters or snail mail, however, the rise of the Internet has provided fraudulent entities with a more streamlined exposure to the overall population.
+According to a Javelin study in 2017, identity frauds hit a record high, targeting 15.4 million victims in the United States \cite{identiytheftonline}.
+The findings indicated that individuals with an online presence were more susceptible to possibility of theft.
+Another recent study released by the  Federal Trade Commission (FTC) reported that debt collection, identity theft, and impostor scams contributed towards 56\% of the total frauds complaints in 2015 \cite{ftcpress2016} .
 With the number of Internet users on the rise, the number of cyber frauds is likely to increase over the next couple of years \cite{perharassment}.
-To deal with the increasing trend, the Federal Bureau of Investigation (FBI), alongside the FTC, has established a similar complaint portal known as the IC3, for the collection of specifically Internet-based fraudulent practices \cite{fbiic3}.
-This emerging trend of deceptive practices necessitates their study in order to evaluate and mitigate the harm caused to victims individuals.
+To deal with this rising situation, the Federal Bureau of Investigation (FBI), has also been actively involved in addressing this issue.
+Their complaint portal, known as the IC3 is specifically designed to record complaints on Internet-based fraudulent practices \cite{fbiic3}.
+This emerging trend of deceptive practices necessitates their study in order to evaluate and mitigate the harm caused to victims.
 
 This paper evaluates the nature of consumer fraud in the United States.
-Our work provides a comparison between cyber and traditional, non-cyber frauds.
-We categorize cyber frauds as all those deceptive practices that victimize users online, while regular ones comprise of frauds that target individuals over the phone, with mail, or in-person.
-While we understand that cyber frauds are a major focus of today's research, our comparison based approach allows us to better understand how they differ from conventional frauds.
-It also enables us to independently evaluate trends in regular frauds and to see whether fraudsters are adopting online mechanisms to target more individuals.
-This combined analysis can enable strategic suggestions to develop better fraud reduction methodologies.
+Our work provides a comparison between cyber and traditional frauds.
+We categorize cyber frauds as all those deceptive practices that victimize users online, while regular (or traditional) ones comprise of frauds that target individuals over the phone, with mail, or in-person.
+While we understand that online scams \cite{miramirkhani2016dial} are a major focus of today's research, our comparison based approach allows us to better understand how they differ from traditional fraud methods.
+It also enables us to independently evaluate trends in traditional frauds and to see whether fraudsters are adopting online mechanisms to target more individuals.
+This combined analysis enables us to provide strategic suggestions in means to develop better fraud reduction methodologies.
 
@@
 We also collect demographic information from the US Census Bureau \cite{uscensus}.
-In addition to data collection, we devise a calibration methodology to identify and separate cyber frauds from non-cyber (regular) in the complaint dataset.
+In addition to data collection, we devise a calibration methodology to identify and separate cyber frauds from regular ones in the complaint dataset.
 
@@
 This encompasses their reporting numbers and methods, the nature of frauds which are more common in each specific category as well as the insights on the fraudsters who carry out these specific deceptive activities.
-Secondly, we look at ethnic, age, education, and employment demographics in each specific category and evaluate if certain individuals are more likely to report crimes.
-Finally, based on our findings we suggest measures that can be taken into account by regulatory agencies to reduce the overall fraud in the United States.
+Secondly, we look at ethnic, age, education, and employment demographics in each specific category and evaluate if certain individuals are more likely to report.
+Finally, based on our findings we suggest measures that can be taken into account by regulatory agencies to reduce overall fraud in the United States.
 
 The rest of the paper is structured as follows, section \ref{related} provides a comprehensive overview of the relevant work.
-In section \ref{data-cal}, we elaborate features of the datasets used in our analysis along with a description of our calibration methodology.
+In section \ref{data-cal}, we elaborate on features of the datasets used in our analysis along with a description of our calibration methodology.
 Section \ref{eval} summarizes our findings from the data, followed by our suggestions to regulatory agencies in \ref{discussion}.
@@
 \centering
-\begin{tabular}{K{0.18\linewidth}|p{0.72\linewidth}}
+\begin{tabular}{K{0.2\linewidth}|p{0.7\linewidth}}
 \hline
@@
 \hline
-Fraud Description & A description of nature the fraud, and its type e.g. credit card, fake product, debt collection.\\
+Fraud Description & Nature of the fraud, and its type e.g. credit card, fake product, debt collection.\\
 \hline
-Fraud \&
+Occurrence \&
  Reporting Date & The dates when the fraud initially occurred and the date on which is was reported.
@@
 
-As our work evaluates both cyber as well as regular frauds, we provide related work that encompasses both of these categories.
+As our work evaluates both cyber as well as regular frauds, we provide related work that encompasses both categories.
 Before the Internet became a primary hub of economic and social activity, researchers measured \cite{clarke2001controlling} and developed techniques based on statistical models \cite{brause1999neural, moreau1997detection, bolton2002statistical} to detect phone and credit card based frauds.
@@
 Even though term \emph{"cyber fraud"} is usually associated with Computer Science, its recent socio-economic impact has motivated researchers in Economics, Law, and Finance to explore solutions by incorporating methodologies specific to their areas.
-Ionescu et.
-al \cite{ionescu2011fraud} characterize the types and sources cyber financial frauds in global digital networks.
-The authors suggest the involvement of all stakeholders and employees through awareness and training for containing and mitigating fraud.
-Similarly, Howard et.
-al \cite{howard2007cyber} study malicious code attacks against financial networks and suggest technical detection and mitigation techniques for financial infrastructure.
-\cite{piper2002} studies how the cyber criminals have several potential advantages over their opposing law enforcement agencies.
-They suggest some practical steps to even out the differential gap.
+Ionescu et al.
+characterize the types and sources of cyber financial frauds in global digital networks \cite{ionescu2011fraud}.
+The authors suggest the involvement of all stakeholders and employees through awareness and training to contain and reduce fraud.
+Similarly, Howard et al.
+study malicious code attacks against financial networks and suggest technical detection and mitigation techniques for financial infrastructure \cite{howard2007cyber} .
+Studies also show how the cyber criminals have several potential advantages over their opposing law enforcement agencies and suggest some practical steps to even out the differential gap \cite{piper2002}.
 
 Due to an increase in the overall concern for online fraudulent activity, there has also been state-sponsored research that measures the impact of fraud.
-Smyth et.
-al \cite{smyth2011measuring} measure the extent of cyber fraud in Canada in 2011.
-Their work indicates that a major chunk of frauds does not get recorded and suggest a need for a sentinel record fraud data, similar to the FTC complaint center in the US.
+Smyth et al.
+measure the extent of cyber fraud in Canada in 2011 \cite{smyth2011measuring}.
+Their work indicates that a major chunk of frauds does not get recorded and hence the suggest a need for a sentinel to record fraud data, similar to the FTC complaint center in the US.
 
-Another significant area of research focuses on understanding the demographics of fraud victims.
-\cite{JOCA:JOCA1}.
-A recent FTC Report \cite{raval2016determines} uses complaint data to quantify complaint rates and across different ethnic and education groups in the US.
-\cite{garrett2010consumers} also look at how demographics effect the likelihood of an individual to complain about fraud.
-Researchers in \cite{ablon2016consumer} provide a comprehensive survey report that sums the reactions of the victims of an online data breach.
+Another significant area of research focuses on understanding the demographics of fraud victims \cite{JOCA:JOCA1}.
+A recent FTC Report \cite{raval2016determines} quantifies complaint rates across different ethnic and education groups in the US.
+Garrett et al also look at how demographics affect the likelihood of an individual to complain about fraud \cite{garrett2010consumers}.
+Researchers have also focused on studying the reactions of the victims of an online data breach \cite{ablon2016consumer}.
 They categorize their results in different income, education, age, and ethnic groups.
@@
 
-In comparison to previous research which individually look at either cyber or regular fraud, our work provides a unique angle of evaluation.
+Contrary to previous research, which individually studies cyber or regular fraud, our work provides a unique angle of evaluation, by comparison of both fraud types.
 We evaluate characteristics for both types of cyber and regular frauds and their demographic trends.
-
 \section{Data and Calibration} \label{data-cal}
 
-In this section we explain the characteristics of our datasets and the sources they were obtained from.
-We also provide insight into the essential data processing and calibration methodology that we incorporate to classify and filter the data for a fair evaluation of our questions.
+In this section, we explain the characteristics of our datasets and the sources they were obtained from.
+We also provide insight into the essential processing and calibration methodology that we incorporate to classify and filter the data for a fair evaluation of our questions.
 
@@
 
-The primary dataset that we use for our evaluation is a corpus of the complaint logs filed at different collections agencies and reported to the FTC during the months Jan 2013 to June 2014.\footnote{This data was obtained from the directly from the FTC under the Freedom of Information Act.} The Dataset is comprised of 865K complaints aggregated for cyber as well as regular fraud instances during the time period.
-Table \ref{ftcdata} shows the fields of the original dataset along with their description summary.
-For the purposes of brevity, we only include the fields that were used in our analysis.
+The primary dataset we use for our evaluation is a corpus of the complaint logs collected between the months of Jan 2013 to June 2014 at agencies within the US and reported to the FTC.
+\footnote{This data was obtained from the directly from the FTC under the Freedom of Information Act (FOIA).} The Dataset is comprised of 865K complaints aggregated for cyber as well as regular fraud.
+Agencies responsible for collecting these logs provide online portals, phone or in-person reporting services.
+Inconsistent reporting semantics is an associated challenge with multiple data collection sources.
+While the FTC data is calibrated to a fair extent, to ensure the accuracy of our results, we perform an initial data consistency parse to exclude irrelevant outliers from the aggregated dataset.
+Table \ref{ftcdata} shows the fields of the used dataset along with their description.
+While the original dataset has several fields, for reader convenience and brevity, we only include the relevant ones form the basis our analysis.
 \\
@@
   \item Population density per zip code
-  \item Education and income data \footnote{We obtained education data from \cite{zipatlas}.}
+  \item Education and income data \footnote{We obtained education data from an aggregator of US demographics \cite{zipatlas}.}
   \item Age statistics
@@
 
-As zip codes provide a low level granularity, to aggregate adjacent zip codes we obtain the Zip codes to the Metropolitan Statistical Area (MSA) mappings from \cite{uslaborstats}.
+As zip codes provide a low-level granularity, to aggregate adjacent zip codes we obtain the Zip codes to the metropolitan Statistical Area (MSA) mappings from \cite{uslaborstats}.
 MSA are essentially groups of geographically connected zip codes that demonstrate strong social and economic linkage.
 While there are more than 40,000 zip codes in the United States there are only 382 distinct MSAs \cite{uscensus}.
+While our analysis in section \ref{demographic_analysis} aggregates different demographics based on zip codes, we incorporate the use of MSAs while performing location based evaluations in section \ref{fraudser_locations}.
+This essentially allows us to cluster the zip codes and associate a named location with them.
+This aggregation also helps mitigate any bias caused by an anomalous outlier zip code.
 
@@
 
-As the FTC dataset was aggregated for all fraud channels a major calibration step we perform is to tag each crime complaint as either cyber or regular.
-An associated challenge for this was our limited view of the fraud description.
+One of the major fundamentals of our comparison is accurate tagging of each complaint as either cyber or regular fraud.
+While having a limited view of the fraud description, this paper takes a \emph{best effort} calibration approach to differentiate between the two types of frauds.
 To perform this calibration we use the \textbf{Contact Method} and \textbf{Fraud Description} fields from Table \ref{ftcdata}.
-We flag a complaint as cyber if the victims primary contact method was through online media; these are primarily websites, social networks, email and IM.
-For the remainder of the complaints we look at the description.
-If the complaint description involves something associated with Internet, we classify it as a cyber fraud regardless of how the victim was initially approached.
-Figure \ref{classify} provides a depiction of our classification methodology.
+Initially, we manually classify all contact methods and descriptions as either cyber or regular.
+We then flag a complaint as cyber if the victim's primary contact method was through online media; these are primarily websites, social networks, email, and IM.
+For the remainder of the complaints, we look at the description.
+If the complaint description involves something associated with the Internet, we classify it as a cyber fraud regardless of how the victim was initially approached.
+For instance, frauds, in which an individual is contacted via phone and requested to perform certain actions on their computer e.g.
+visiting a certain website, will be categorized as cyber.
+While this is a sophisticated technique that involves phone communication, the actual fraud hinges on the victim performing specific actions online, making it cyber nature.
+Figure \ref{classify} provides a visualization of our keyword classification methodology.
 This process provides us with two distinct categories and enables a fair comparison of the frauds.
@@
 \subsection{Fraud Reporting Methods}\label{reportingmethods}
+
 Consumers have the ability to report complaints to the FTC via several methods and agencies.
@@
 
-\subsection{Top Fraudster Locations}\label{fraudsters}
+\subsection{Top Fraudster Locations}\label{fraudser_locations}
 Next, we identify the primary locations of the fraudsters within the United States and present our findings in \ref{topareas}.
@@
 
-\subsection{Demographic Analysis}\label{fraudsters}
+\subsection{Demographic Analysis}\label{demographic_analysis}
 
@@
 
+\section{Acknowledgments}\label{Acknowledgments}
+
 \bibliographystyle{IEEEtran}

### 2017-03-08 paper/paper.tex
addressed reviewer concerns

@@
 \vspace{8pt}
-\caption{Summary Statistics of the FTC dataset}\label{ttest}
+\caption{Summary Statistics of the FTC dataset}\label{summary_stats}
 \vspace{-10pt}
@@
 
-The primary dataset we use for our evaluation is a corpus of the complaint logs collected between the months of Jan 2013 to June 2014 at agencies within the US and reported to the FTC.
-\footnote{This data was obtained from the directly from the FTC under the Freedom of Information Act (FOIA).} The Dataset is comprised of 865K complaints aggregated for cyber as well as regular fraud.
+The primary dataset we use for our evaluation is a corpus of the complaint logs collected between the months of Jan 2013 to June 2014 at agencies within the US and reported to the FTC\footnote{This data was obtained from the directly from the FTC under the Freedom of Information Act (FOIA).}.
+The Dataset is comprised of 865K complaints aggregated for cyber as well as regular fraud.
 Agencies responsible for collecting these logs provide online portals, phone or in-person reporting services.
@@
 While the original dataset has several fields, for reader convenience and brevity, we only include the relevant ones form the basis our analysis.
+we also provide summary statistics of the data in table \ref{summary_stats}.
 \\
+
 \subsubsection{US Census Datasets}
@@
 
-Our evaluation section can be divided into three main components.
-First, we look at the different aspects and trends within the complaint dataset and elaborate on certain prominent characteristics between regular and cyber frauds.
-Next we study consumer and fraudster behaviors.
-The third part of our evaluation focuses on an in-depth analysis of the demographics linked with the fraud types.
+Having the categorized dataset, we aim to answer the primary question of how cyber and regular fraud compare to each other Based on the auxiliary information in the  FTC dataset, combined with the informative fields from secondary sources, we are able to explore various data dimensions for our cpmparison.
+First, we look at how cyber and regular crimes vary across the different times of the year.
+We then aim to understand the distribution of cyber and regular frauds across victims.
+We also compare the reaction of the targeted individuals by evaluating their respective reporting methods and reaction time.
+Similarly, we explore if fraudsters of cyber and regular frauds have certain distinguishable characteristics.
+Finally, we provide an in-depth comparison of various demographics for the two fraud types.
 
-\subsection{Fraud Variation over Time}
+\subsection{Fraud Variation over Time}\label{var_time}
 
-\begin{table}[b]
+We initially perform a temporal analysis of the 15-month dataset to evaluate how the fraud reporting varies over time and explore when a certain type of frauds is more likely to be reported.
+We use the reporting date as an estimate of fraud count on that specific date.
+While the overall rate of fraud remains consistent, we observe a significant reduction in reporting in the winter holiday season.
+To investigate this, we select two distinct, 20 day periods in the dataset; we label them as \textbf{Working} (Aug, 15  to Sept, 5) and \textbf{Holiday} (Dec 15, to Jan, 5).
+Figure \ref{temporal} shows the variation of cyber and regular frauds within the two specific time periods.
+We observe a significant drop in the frauds during the holiday time period.
+Individually, cyber fraud decreases by 26\% while regular fraud decreases by a much larger value of 56\%.
+Our analysis is based on the conservative assumption that, reporting count on a date positively correlates with the number of frauds and there is not a significant reporting delay between the crime and reporting dates.
+We validate this in figure \ref{cdffig} (a), which shows that approximately 70\% of reporting dates are within a week of the date when the incident occurred, we also suggest some associated limitations to this approach in section \ref{reaction_time}.
+We also believe that the larger decrease in regular frauds is an overestimate as result of a bias that we explain using additional statistical findings from the next section.
+
+\begin{figure}[t]
+\centering
+  \includegraphics[scale=0.35]{graphics/reg_vs_holiday.pdf}
+  \caption{Fraud reporting incidence during regular and holiday season}
+  \label{temporal}
+\end{figure}
+
+\subsection{Fraud Reporting Methods}\label{reportingmethods}
+
+Consumers have the ability to report complaints to the FTC via several methods and agencies.
+We aggregate the 26 complaint collecting entities into online and offline categories.
+For instance, reports made via the Internet complaint center or the FTC complaint assistant are tagged as online, while the ones issued to the FTC call center, publisher clearing house, attorneys general, or other regulatory institutions are categorized as offline.
+Figure \ref{reportingfig} provides the distribution of how individuals opt to report cyber and regular crimes.
+Approximately 82\% of cyber fraud victims used an online complaint facility, and 63\% of regular fraud victims reported via offline methods.
+
+We observe that a major chunk of regular frauds is reported to offline institutions, which have reduced operation during holidays.
+We believe this significantly contributes to the reduction bias of the value of regular frauds in figure \ref{temporal}.
+
+ \begin{figure}[t]
+\centering
+  \includegraphics[scale=0.35]{graphics/reporting_methods.pdf}
+  \caption{Distribution of reporting methods for frauds}
+  \label{reportingfig}
+\end{figure}
+
+To further validate this, we perform a two-sample t-test over the distribution of fraud reports for both cyber and regular frauds.
+The compared distributions belong to the working and holiday period explained in section \ref{var_time}.
+Our null hypothesis assumes that both time periods belong to the same reporting pool.
+The statistically significant \emph{p-value} for regular frauds in table \ref{ttest} suggests in favor of the alternative hypothesis, hence validating our assumed bias for a decrease in regular frauds.
+Additionally, we also calculate the percent increase in reporting between the last 10 holidays and 10 working days right after.
+While cyber reports only increase by 37\% the increase in regular fraud reports is a staggering 104\%.
+The ratio of increases is in line with the proportions (17:66) for offline reporting methods used by cyber and regular fraud victims.
+We believe that while both types of frauds experience a decrease, the decrease in cyber frauds represents a more accurate trend.
+These derived insights enable us to suggest more meaningful measures in section \ref{discussion} to deal with consumer fraud.
+
+\vspace{-8pt}
+
+\begin{table}[h]
 \centering
@@
 \hline
-\multicolumn{1}{c}{\bfseries Fraud Type} & \multicolumn{1}{c}{\bfseries \emph{p-value}
-Coefficient}
+\multicolumn{1}{c}{\bfseries Fraud Type} & \multicolumn{1}{c}{\bfseries \emph{p-value}}
 \\
@@
 
-We initially perform a temporal analysis of the 15-month dataset to evaluate how the fraud reporting varies, over time and explore when a certain fraud is more likely to be reported.
-As a limitation of our dataset\footnote{The dataset had significant missing values for the date if initial contact of fraud, Figure \ref{reportingfig} (a) shows that approximately 70\% of reporting dates were within a week of the date when the incident occurred.}, we use the reporting date as an estimate of fraud count for a specific date.
-While the overall rate of fraud remains consistent, we observe significant variations in the winter holiday season.
-To investigate this, we select two distinct, 20 day periods in the dataset; we label them as \textbf{Working} (Aug, 15  to Sept, 5) and \textbf{Holiday} (Dec 15, to Jan, 5).
-Figure \ref{temporal} shows the variation of cyber and regular frauds within the two specific time periods.
-We observe a significant drop in the frauds during the the holiday time period.
-Individually, cyber fraud decreases by 26\% while  regular fraud decreases by a much larger value of 56\%.
-We believe that the larger decrease in regular frauds is an overestimate as result of a bias that we explain using additional findings from the next section.
+\subsection{Consumer Reaction Time}\label{reaction_time}
 
-\begin{figure}[t]
-\centering
-  \includegraphics[scale=0.35]{graphics/reg_vs_holiday.pdf}
-  \caption{Fraud variation during regular and holiday season}
-  \label{temporal}
-\end{figure}
-
-\subsection{Fraud Reporting Methods}\label{reportingmethods}
-
-Consumers have the ability to report complaints to the FTC via several methods and agencies.
-We aggregate the 26 complaint collecting entities into online and offline categories.
-For instance, reports made via the Internet complaint center or the FTC complaint assistant are tagged as online, while the ones issued to the FTC call center, publisher clearing house, attorney generals, or other regulatory institutions are categorized as offline.
-Figure \ref{reportingfig} provides the distribution of how individuals opt to report cyber and regular crimes.
-Approximately 82\% of cyber fraud victims used an online complaint facility, and 63\% of regular fraud victims reported via offline methods.
-
- \begin{figure}[b]
-\centering
-  \includegraphics[scale=0.35]{graphics/reporting_methods.pdf}
-  \caption{Distribution of reporting methods for frauds}
-  \label{cdffig}
-\end{figure}
-
-A major chunk of regular frauds are reported to offline institutions which have reduced operation during holidays.
-We believe this significantly contributes to the reduction bias of regular frauds value in Figure \ref{temporal}.
-To further validate this bias, we perform a t-test for the two fraud categories across the working and holiday time periods.
-The statistically significant \emph{p-value} for regular frauds in Table \ref{ttest} rejects our null hypothesis of \emph{identical reporting trends across the two time periods}.
-Additionally, we also calculate the percent increase in reporting between the last 10 holidays and 10 working days right after.
-While cyber reports only increase by 37\% the increase in regular fraud reports is a staggering 104\%.
-The ratio of increases is in line with the proportions (17:66) for offline reporting methods used by cyber and regular fraud victims.
-We believe that while both types of frauds experience a decrease, the decrease in cyber frauds represents a more accurate trend.
-These derived insights enable us to suggest more meaningful measures in section \ref{discussion} to deal with consumer fraud.
-
-\subsection{Consumer Reaction Time}\label{fraudsters}
-
-We evaluate how quickly do the victims of a fraud report an incident.
+Here we evaluate on how quickly do victims of a fraud react and report the incident.
 Figure \ref{cdffig} (a) shows the CDF of the number of days between the date when the fraud occurred and when in was first reported to the FTC.
@@
 We believe that this provides ample time window for fraudsters to maliciously act on the assets acquired from individuals.
-This increased delay can also be a result of individuals discovering they were victimized to a fraud at a later date than the actual incident.
-One example would be of a credit card theft, when the victims only recognize the breach after they see an unauthorized transaction.
-Unfortunately, we do have enough information in the dataset to normalize against this trend.
-
-\subsection{Most Common Frauds}\label{fraudsters}
-
-Table \ref{topfrauds} provides a summary of the top frauds in each category.
-The significant cyber presence of impostor scams and sweepstakes in, which have long existed in the regular fraud domain, provides evidence that fraudsters are adopting new technology to execute the same frauds.
-We incorporate this specific insight in our discussion in section.
-Our results greatly align with the top sources of frauds stated in an FTC news release in 2016 \cite{ftcpress2016}.
+This increased delay can also be a result of individuals discovering they were victimized by a fraud at a later date than the actual incident.
+One example would be a credit card theft when the victims only recognize the breach after they see an unauthorized transaction.
+Unfortunately, we do have enough information in the dataset to normalize in against such a situation in practice.
 
@@
 
-\subsection{Top Fraudster Locations}\label{fraudser_locations}
-Next, we identify the primary locations of the fraudsters within the United States and present our findings in \ref{topareas}.
-While fraudulent entities are spread throughout, most of the heavy hitters belong to the metropolitan areas.
-We believe this provides an efficient disguise to the fraudulent entities.
+\begin{figure}[t]
+\centering
+  \includegraphics[scale=0.28]{graphics/dist_days.pdf}
+  \caption{The cumulative distribution for (a) The difference between fraud and reporting dates. (b) The distance between consumers and fraudsters.}
+  \label{cdffig}
+\end{figure}
+
+\subsection{Most Common Frauds}\label{fraudsters}
+
+By using the fraud description fields we summarize the the top frauds in table
+
+\ref{topfrauds} provides a summary of the top frauds in each category.
+
+We see a significant cyber presence of impostor scams and sweepstakes.
+While these frauds have long existed in the regular domain, this provides us anecdotal evidence that fraudsters are adopting new technology to execute the same types of scams online, which were previously perpetrated offline.
+We incorporate this specific insight in our discussion.
+Our results greatly align with the top sources of frauds stated in an FTC news release in 2016 \cite{ftcpress2016}.
+
+\subsection{Fraudster Coverage}\label{fraudstercoverage}
+
+In order to understand the operational regions of fraudulent entities, we calculate the distances between consumer and fraudster zip codes.
+Figure \ref{cdffig} (b) provides a cumulative distribution of the operational radii for cyber and regular fraudsters.
+This analysis provides insight on whether cyber fraudsters leverage the Internet for more visibility and access to target more distant individuals.
+With a median distance of 993 and 861 for cyber and regular frauds, we believe that both types of fraudsters follow similar trends.
+This indicates that Internet-based communication does not provide cyber fraudsters with a significant advantage over regular ones, as they are able to achieve similar operational spans by using phone and mail based communication methods.
 
@@
 
-We also observe certain areas that have a high cyber to regular fraud ratio and vice versa.
+\subsection{Top Fraudster Locations}\label{fraudser_locations}
+Next, we identify the primary locations of the fraudsters within the United States and present our findings in \ref{topareas}.
+While fraudulent entities are spread throughout, most of the heavy hitters belong to the metropolitan areas.
+We believe this provides an efficient disguise to the fraudulent entities.
+We also observe certain areas that having a high cyber to regular fraud ratio and vice versa.
 The San Franciso, Oakland and San Jose, Santa Clara MSAs have a cyber to regular fraud ratio of 2.21 and 5.13.
@@
 Meanwhile, The Buffalo, Niagara Falls MSA has a regular to cyber fraud ratio of 8.76 with debt collection being the significant outlier.
-Further investigation reveals that Buffalo has a network of debt collecteors which have been responsible for multi-million frauds \cite{buffalodebt1, buffalodebt2}.
+Further investigation reveals that Buffalo has a network of debt collectors which have been responsible for multi-million frauds \cite{buffalodebt1, buffalodebt2}.
 
-\subsection{Fraudster Coverage}\label{fraudstercoverage}
+\subsection{Demographic Analysis}\label{demographic_analysis}
 
-In order to understand the operational regions of fraudulent entities, we calculate the distances between consumer and fraudster zip codes.
-Figure \ref{reportingfig} (b) provides a cumulative distribution of the operational radii for cyber and regular fraudsters.
-This analysis provides insight on whether cyber fraudsters leverage the Internet for more visibility and access to target more distant individuals.
-With a median distance of 993 and 861 for cyber and regular frauds, we believe that both types of fraudsters follow similar trends.
-This indicates that a major the Internet based communication does not provide cyber fraudsters with significant advantage over regular ones as they are able to achieve similar operational spans by using phone and mail based communication methods.
+By normalizing over cyber and regular frauds in each zip code, we evaluate how they vary with certain demographic features, which are obtained from the complementary datasets that we discuss in section \ref{data-cal}.
+
+To realize the effect of these features, we perform a logistic regression and summarize our coefficients and their significances in table \ref{regressions}.
+Among different ethnicities, only Hispanic communities show statistically significant change for cyber and regular fraud per capita.
+While the regression coefficients suggest that frauds decrease for heavier concentrations of  Hispanics, a survey study \cite{anderson2013consumer} showed that Hispanics and Black communities are more likely to be victims of crimes.
+The decreasing trend is likely a result of fraud under-reporting due to cultural reasons, distrust in institutions, and lack of awareness or education \cite{consumerlessons}.
+
+Other socio-economic variables that we take into account are age, income, education, and unemployment rate.
+In addition to the regression analysis, we investigate their variation by observing complaint rates across their distributions in figure \ref{demographics}.
+
+\textbf{Age:} While the differences in cyber and regular complaints remain fairly consistent, from figure \ref{demographics} (a) we observe that individuals greater that 50 years complain significantly more than other age groups.
+Our significant regression values also corroborate to this trend.
+
+\textbf{Education:} Both cyber and regular complaints increase along with an increase in percentage education.
+We associate this trend with greater increased educational awareness among individuals \cite{consumerlessons}.
+Another subtle trend, in the increase in cyber to regular complaint ratio from 0.82 to 1.23.
+We associate this diverging trend to more educated individuals being active on the Internet, and hence being more prone to online fraud~\cite{pewcollege}.
+
+We do not include income and unemployment in our analysis due to their insignificant correlation values in table \ref{regressions}.
 
@@
 \centering
-  \includegraphics[scale=0.28]{graphics/dist_days.pdf}
-  \caption{The cumulative distribution for (a) The difference between fraud and reporting dates. (b) The distance between consumers and fraudsters.}
-  \label{reportingfig}
+  \includegraphics[scale=0.29]{graphics/demographics.pdf}
+  \caption{Cyber and regular fraud trends over age, income, education and unemployment.}
+  \label{demographics}
 \end{figure}
-
-\subsection{Demographic Analysis}\label{demographic_analysis}
 
@@
 \end{tabular}
-
 \vspace{8pt}
@@
 \end{table*}
-
-\begin{figure}[b]
-\centering
-  \includegraphics[scale=0.29]{graphics/demographics.pdf}
-  \caption{Cyber and regular fraud trends over age, income, education and unemployment.}
-  \label{demographics}
-\end{figure}
-To evaluate the effect of prominent demographic features we perform a logistic regression for both cyber and regular complaint rates.
-Table \ref{regressions} summarizes our coefficients and their significance.
-Among ethnicities, our results generate statistically significant results for only Hispanic communities.
-While the coefficients suggest that frauds decrease for heavier concentrations of  Hispanics, a survey study \cite{anderson2013consumer} showed that Hispanics and Black communities are more likely to be victims of crimes.
-The decreasing trend is likely a result of fraud under-reporting due to cultural reasons, distrust in institutions, and lack of awareness or education \cite{consumerlessons}.
-
-Other socio-economic variables that we take into account are age, income, education an the rate of unemployment.
-In addition to the regression analysis, we investigate their variation by observing complaint rates across their distributions in Figure \ref{demographics}.
-
-\textbf{Age:} While the differences in cyber and regular complaints remain fairly consistent, from Figure \ref{demographics} (a) we observe that individuals greater that 50 years complain significantly more than other age groups.
-Our significant regression values also corroborate to this trend.
-
-\textbf{Education:} Both cyber and regular complaints increase along with an increase in percentage education.
-We associate this trend with greater increased educational awareness among individuals \cite{consumerlessons}.
-Another subtle trend, in the increase in cyber to regular complaint ratio from 0.82 to 1.23.
-We associate this diverging trend to more educated individuals being active  the Internet  more frequently, and hence being more prone to online fraud~\cite{pewcollege}.
-Our reasoning is in line with insights from our regression analysis which additionally normalizes for other factors.
-
-We do not include income and unemployment in our analysis due to their insignificant correlation values in Table \ref{regressions}.
 
@@
 The fraudulent cyber establishments of San Jose and San Francisco discussed in Section \ref{fraudsters}, help us understand that fraudulent entities likely reflect the makeup of nearby legitimate industries.
+
 By observing the overlap between top cyber and regular frauds (Table \ref{topfrauds}) we realize that with the rise of Internet, fraudsters have their choice of vectors to execute scams that were traditionally only perpetrated through traditional means.
-Better understanding these advanced communication  modalities requires a technologists' touch;  policy makers should consider working closely with technologists to devise detection mechanisms similar to \cite{brause1999neural, moreau1997detection} which enable better filtering and control of fraudulent activity.
+Better understanding these advanced communication modalities requires a technologists' touch;  policy makers should consider working closely with technologists to devise detection mechanisms similar to \cite{brause1999neural, moreau1997detection} which enable better filtering and control of the fraudulent activity.
 
-\section{Conclusion}\label{conclusion}
+\section{Conclusion \& Future Work}\label{conclusion}
 
@@
 
+Fraud analysis is an impactful topic that has been understudied in academia.
+While our current work has its limitations, we plan to extend our analysis over multiple years by establishing a collaboration with the FTC and obtaining high fidelity datasets that span a longer duration.
+We also look forward to evaluating our current findings with data collected by other regulatory agencies such as the FBI.
+This will eventually also allow us to overcome certain nuances and limitations of the current evaluation and help us develop stronger insights.
+Another interesting future direction is to evaluate how international fraud compares to fraud within the US, and identify any prominent international fraudsters who target US victims.
+This can possibly be achieved by using data from the European Commission and the eCrime project.
+
 \section{Acknowledgments}\label{Acknowledgments}
+
+We would like to thank the reviewers of the workshop for
+reviewing our work and providing helpful feedback.
 

### 2017-03-12 paper/paper.tex
tiny fixes

@@
 
-\title{Old is Still Gold: A Comparison of Cyber and Regular Consumer Fraud in The United States}
+\title{Old is Still Gold: A Comparison of Cyber and Traditional Consumer Fraud in The United States}
 
@@
 cyber and traditional categories, we summarize the difference in fraud
-trends across time, distance and location metrics.We also evaluate fraud
-variations across different ethnic and socio-economic factors. Our findings
-suggest that both categories of frauds experience an overall decrease during
+trends across time, distance and location metrics. We also evaluate fraud
+variations across different ethnic and socioeconomic factors. Our findings
+suggest that reports of both categories of frauds decrease during
 the holiday season. Individuals who are victimized via traditional methods
@@
 
-We would like to thank the reviewers of the workshop for
-reviewing our work and providing helpful feedback.
+We would like to thank the reviewers for reviewing our work and providing
+helpful feedback. This material is based upon work supported by the National Science Foundation
+ under Grant No. 1351058. Any opinions,
+findings, and conclusions or recommendations expressed in this material are
+those of the authors and do not necessarily reflect the views of the
+National Science Foundation.
 

### 2017-03-13 paper/paper.tex
full intro/conclusion pass

@@
 While cybercrime is a relatively recent human invention, fraudulent activity
-has a much longer history.
-Understanding the extent to which cybercrime is fundamentally different from, or similar to, traditional fraudulent activity is the first step toward being able to effectively combat it.
-This paper investigates the differences in fraud
-reporting and targeting among United States based consumers by comparing
-fraudulent activity mediated by the Internet with traditional forms of
-fraud. By partitioning the FTC Consumer Sentinel complaint dataset into
-cyber and traditional categories, we summarize the difference in fraud
-trends across time, distance and location metrics. We also evaluate fraud
-variations across different ethnic and socioeconomic factors. Our findings
-suggest that reports of both categories of frauds decrease during
-the holiday season. Individuals who are victimized via traditional methods
-are more likely to complain using traditional methods, while a majority of
-cyber victims submit fraud complaints online. By evaluating the top frauds
-in each category, we demonstrate how traditional fraudsters have evolved in
-their methodologies to execute scams on the Internet that were initially
-perpetrated through traditional means.
+has a much longer history. Understanding the extent to which cybercrime is
+fundamentally different from, or similar to, traditional fraudulent activity is
+the first step toward being able to effectively combat it. This paper
+investigates the differences in fraud targeting among United States based
+consumers by comparing reports of fraudulent activity mediated by the Internet
+with traditional forms of fraud. By partitioning the FTC Consumer Sentinel
+complaint dataset into cyber and traditional categories, we summarize the
+difference in fraud trends across time, distance and location metrics. We also
+evaluate fraud variations across different ethnic and socioeconomic factors.
+Our findings suggest that reports of both categories of frauds decrease during
+the holiday season. Individuals who are victimized via traditional methods are
+more likely to complain using traditional methods, while a majority of cyber
+victims submit fraud complaints online. By evaluating the top frauds in each
+category, we demonstrate how traditional fraudsters have evolved in their
+methodologies to execute scams on the Internet that were initially perpetrated
+through traditional means.
 
@@
 
-In the United States, a total of more than 25 million people are victims of frauds per year \cite{anderson2013consumer}.
-These deceptive scams are a major cause of economic damages to users, not to mention the added externalities of wasted time and stress.
-Such illicit practices have been a part of the underground economy for quite a while.
-Initially, individuals were tricked by scam calls, in-person fraudsters or snail mail, however, the rise of the Internet has provided fraudulent entities with a more streamlined exposure to the overall population.
-According to a Javelin study in 2017, identity frauds hit a record high, targeting 15.4 million victims in the United States \cite{identiytheftonline}.
-The findings indicated that individuals with an online presence were more susceptible to possibility of theft.
-Another recent study released by the  Federal Trade Commission (FTC) reported that debt collection, identity theft, and impostor scams contributed towards 56\% of the total frauds complaints in 2015 \cite{ftcpress2016} .
-With the number of Internet users on the rise, the number of cyber frauds is likely to increase over the next couple of years \cite{perharassment}.
-To deal with this rising situation, the Federal Bureau of Investigation (FBI), has also been actively involved in addressing this issue.
-Their complaint portal, known as the IC3 is specifically designed to record complaints on Internet-based fraudulent practices \cite{fbiic3}.
-This emerging trend of deceptive practices necessitates their study in order to evaluate and mitigate the harm caused to victims.
+In the United States, a total of more than 25 million people are victims of
+frauds per year \cite{anderson2013consumer}. These deceptive scams are a major
+cause of economic damages to users, as well as added stress and wasted time.
+Such illicit practices have been a part of the underground economy for quite a
+while. Initially, individuals were contacted via scam calls,  snail mail, or in
+person communication.  The rise of the Internet has provided fraudulent
+entities with a more effective method of communicating with the overall
+population. According to a Javelin study in 2017, identity frauds hit a record
+high, targeting 15.4 million victims in the United
+States~\cite{identiytheftonline}. The findings indicated that individuals with
+an online presence were more susceptible to possibility of theft. Another
+recent study released by the  Federal Trade Commission (FTC) reported that debt
+collection, identity theft, and impostor scams contributed towards 56\% of the
+total frauds complaints in 2015 \cite{ftcpress2016} . With the number of
+Internet users on the rise, the number of cyber frauds is likely to increase
+over the next couple of years \cite{perharassment}. To deal with this rising
+situation, the Federal Bureau of Investigation (FBI), has also been actively
+involved in addressing this issue. Their complaint portal, known as the IC3 is
+specifically designed to record complaints on Internet-based fraudulent
+practices \cite{fbiic3}. This emerging trend of deceptive practices
+necessitates their study in order to evaluate and mitigate the harm caused to
+victims.
 
-This paper evaluates the nature of consumer fraud in the United States.
-Our work provides a comparison between cyber and traditional frauds.
-We categorize cyber frauds as all those deceptive practices that victimize users online, while regular (or traditional) ones comprise of frauds that target individuals over the phone, with mail, or in-person.
-While we understand that online scams \cite{miramirkhani2016dial} are a major focus of today's research, our comparison based approach allows us to better understand how they differ from traditional fraud methods.
-It also enables us to independently evaluate trends in traditional frauds and to see whether fraudsters are adopting online mechanisms to target more individuals.
-This combined analysis enables us to provide strategic suggestions in means to develop better fraud reduction methodologies.
+This paper evaluates the nature of consumer fraud in the United States. Our
+work provides a comparison between cyber and traditional frauds. We categorize
+cyber frauds as all those deceptive practices that victimize users online,
+while regular (or traditional) frauds target individuals over the phone, via
+mail, or in-person. While we understand that online
+scams~\cite{miramirkhani2016dial} are a major focus of today's research, our
+comparison based approach allows us to better understand how they differ from
+traditional fraud methods. It also enables us to independently evaluate trends
+in traditional frauds and to determine whether fraudsters are adopting online
+mechanisms to target more individuals. This combined analysis enables us to
+provide strategic suggestions in means to develop better fraud prevention
+techniques.
 
 To evaluate fraud trends, we use the FTC's Consumer Sentinel database, a dataset of complaints from the year 2013 and 2014.
-We also collect demographic information from the US Census Bureau \cite{uscensus}.
+We also collect demographic information from the US Census Bureau~\cite{uscensus}.
 In addition to data collection, we devise a calibration methodology to identify and separate cyber frauds from regular ones in the complaint dataset.
@@
 
-The goal of this paper is to investigate the dynamics of cyber and traditional methods for committing fraud in the United States.
-By partitioning the FTC Consumer Sentinel complaint dataset, we are able to explore trends among cyber and regular fraud, and analyze trends along time, distance and location metrics as well as their variation across consumer demographics.
-While the Internet has greatly expanded the potential reach and scale of fraudsters: where once they could only use mail or telephones for various frauds, the Internet enables one to contact millions of users very quickly, whether through fraudulent websites, Craigslist posts, or spam emails.
-Even so, the difference between the cyber and non-cyber methodologies is not overwhelming: this effect suggests that non-cyber activities, like purchasing goods or posting money orders, may still serve as a limiting factor on the extent or targeting of these fraudulent activities.
+The goal of this paper is to investigate the dynamics of cyber and traditional
+methods for committing fraud in the United States. By partitioning the FTC
+Consumer Sentinel complaint dataset, we are able to explore trends among cyber
+and regular fraud, and analyze trends along time, distance and location metrics
+as well as their variation across consumer demographics. The Internet has
+greatly expanded the potential reach and scale of fraudsters, enabling them
+to contact millions of users very quickly, whether through fraudulent websites,
+Craigslist posts, or spam emails. Even so, the difference between the cyber and
+non-cyber methodologies is not overwhelming: this effect suggests that
+non-cyber activities, like purchasing goods or posting money orders, may still
+serve as a limiting factor on the extent or targeting of these fraudulent
+activities.
 
-Fraud analysis is an impactful topic that has been understudied in academia.
-While our current work has its limitations, we plan to extend our analysis over multiple years by establishing a collaboration with the FTC and obtaining high fidelity datasets that span a longer duration.
-We also look forward to evaluating our current findings with data collected by other regulatory agencies such as the FBI.
-This will eventually also allow us to overcome certain nuances and limitations of the current evaluation and help us develop stronger insights.
-Another interesting future direction is to evaluate how international fraud compares to fraud within the US, and identify any prominent international fraudsters who target US victims.
-This can possibly be achieved by using data from the European Commission and the eCrime project.
+As a future effort in this space, we plan to extend our analysis over multiple
+years through analysis of different, higher fidelity datasets that span a
+longer duration. We also look forward to evaluating our current findings with
+data collected by other regulatory agencies such as the FBI. This will
+eventually also allow us to overcome certain nuances and limitations of the
+current evaluation and help us develop stronger insights. Another interesting
+future direction is to evaluate how international fraud compares to fraud
+within the US, and identify any prominent international fraudsters who target
+US victims. This can possibly be achieved by using data from the European
+Commission and the eCrime project.
 
@@
 
-We would like to thank the reviewers for reviewing our work and providing
-helpful feedback. This material is based upon work supported by the National Science Foundation
- under Grant No. 1351058. Any opinions,
-findings, and conclusions or recommendations expressed in this material are
-those of the authors and do not necessarily reflect the views of the
-National Science Foundation.
+We would like to thank the reviewers for their helpful feedback. This material
+is based upon work supported by the National Science Foundation under Grant No.
+1351058. Any opinions, findings, and conclusions or recommendations expressed
+in this material are those of the authors and do not necessarily reflect the
+views of the National Science Foundation.
 
